\section{Summary TL;DR} \label{sec:tldr} \begin{itemize} \item The internet may be undergoing a transformation, driven by trust abuses by incumbent providers, and popularization of concepts like Web3 and the Metaverse. \item Current large scale `social' and immersive metaverse platforms have low adoption, while more advanced games-based solutions don't address societal or business needs. \item Platforms like Roblox, VRChat, and Nvidia Omniverse emerge as potential contenders in the metaverse landscape. \item Distributed compute and large language models can help bridge the digital divide by enhancing global access equity and addressing the needs of emerging markets and less developed nations. \item The potential lies in uniting individual ecosystems with transferable goods across digital society through global ledgers like blockchain, despite the associated risks and uncertainties. \item Industry is looking towards an "open metaverse" to mitigate risks observed in implementations like Meta, necessitating contributions of open-source and federated approaches in telecollaboration research. \item By embracing Nostr protocol, we could enable connections and federation of mixed reality spaces, mediate data synchronization, and maintain secure communication. \item AI, machine learning, and generative art play a crucial role in driving innovation, with models like GPT4, Llama, Alpaca, generating excitement, and deepening global discussions around AI. \item Overcoming legislative and cultural barriers, alongside integrating large language models and distributed compute, can help address issues related to trust, accessibility, governance, and safeguarding within the metaverse and digital society at large. \item Open-source tools for supported creativity and augmented intelligence using multi-modal models, can help tackle accessibility, creativity, language barriers, and governance within the metaverse landscape. \item The application of these tools can lead to the development of new collaborative frameworks across various sectors such as training, research, biomedical, creative industries. \item By utilizing these new AI-driven technologies and emphasizing on trust, accessibility, and open-source approaches, we can create a more inclusive, global digital society while promoting technological empowerment and expansion of the global ideas market. \end{itemize}