\begin{itemize}
\item
  \href{https://github.com/Vision-CAIR/ChatCaptioner}{Interactive photo
  and video scene description}
\item
  \protect\hypertarget{show1_1}{}{+} \protect\hypertarget{hide1_1}{}{-}
  unsorted links
  \begin{itemize}
  \item
    \href{https://github.com/huggingface/diffusers/blob/main/examples/dreambooth/train_dreambooth.py)\%20script...}{Dreambooth
    original links}
  \item
    \begin{itemize}   
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/11ol47u/3d_model_face_color_map_generation_test3/}{3D
      model face color map generation test3 : r/StableDiffusion}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      {[}\url{https://www.reddit.com/r/StableDiffusion/comments/11mulj6/quality_improvements_to_dpm_2m_karras_sampling/\%5D(}\url{https://www.reddit.com/r/StableDiffusion/comments/11mulj6/quality_improvements_to}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      {[}\url{https://www.reddit.com/r/StableDiffusion/comments/11mulj6/quality_improvements_to_dpm_2m_karras_sampling/\%5D(}\url{https://www.reddit.com/r/StableDiffusion/comments/11mulj6/quality_improvements_to}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/114dxgl/advanced_advice_for_model_training_finetuning_and/}{Advanced
      advice for model training / fine-tuning and captioning :
      r/StableDiffusion}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/114dxgl/advanced_advice_for_model_training_finetuning_and/}{Advanced
      advice for model training / fine-tuning and captioning :
      r/StableDiffusion}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/11qexu0/animate_your_stable_diffusion_portraits/\#}{Animate
      your stable diffusion portraits : r/StableDiffusion}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/11qexu0/animate_your_stable_diffusion_portraits/\#}{Animate
      your stable diffusion portraits : r/StableDiffusion}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://github.com/dk-liang/Awesome-GPT-4-with-Applications}{Awesome
      GPT-4 with Applications bar{} Curated list of research,
      applications and libraries for GPT-4}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://github.com/dk-liang/Awesome-GPT-4-with-Applications}{Awesome
      GPT-4 with Applications bar{} Curated list of research,
      applications and libraries for GPT-4}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://buff.ly/3laNpgY}{Face manipulation}
    \end{itemize}

    \begin{itemize}
     
    \item
      Other
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://buff.ly/3laNpgY}{Face manipulation}
    \end{itemize}

    \begin{itemize}
     
    \item
      Other
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://github.com/lxe/simple-llama-finetuner}{GitHub -
      lxe/simple-llama-finetuner: Simple UI for LLaMA Model Finetuning}
    \end{itemize}

    \begin{itemize}
     
    \item
      Other. The text is a description of a conference called "Toward a
      Science of Consciousness," which covers a range of topics related
      to consciousness studies.
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \url{https://3d-diffusion.github.io/}
    \end{itemize}

    \begin{itemize}
     
    \item
      This is a machine learning text that discusses a 3D generation
      model called 3DiM. The model is designed to take a single input
      view and generate consistent and sharp completions across many
      views.
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \url{https://mobile.twitter.com/nic__carter/status/1635328056234766337}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \url{https://www.reddit.com/r/StableDiffusion/comments/11owo31/something_that_might_help_ppl_with_posing/}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \url{https://www.reddit.com/r/StableDiffusion/comments/11pyiro/new_feature_zoom_enhance_for_the_a111_webui/}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \url{https://www.reddit.com/r/StableDiffusion/comments/11pyiro/new_feature_zoom_enhance_for_the_a111_webui/}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://techoversight.org/2023/03/20/memo-tiktok-is-a-threat-so-is-the-rest-of-big-tech/}{MEMO:
      TikTok is a threat. So is the rest of Big Tech. - Tech Oversight
      Project}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://techoversight.org/2023/03/20/memo-tiktok-is-a-threat-so-is-the-rest-of-big-tech/}{MEMO:
      TikTok is a threat. So is the rest of Big Tech. - Tech Oversight
      Project}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.marktechpost.com/2023/03/10/open-ai-proposes-consistency-models-a-new-family-of-generative-models-that-achieve-high-sample-quality-without-adversarial-training/}{Open
      AI Proposes Consistency Models: A New Family of Generative Models
      That Achieve High Sample Quality Without Adversarial Training -
      MarkTechPost}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.marktechpost.com/2023/03/10/open-ai-proposes-consistency-models-a-new-family-of-generative-models-that-achieve-high-sample-quality-without-adversarial-training/}{Open
      AI Proposes Consistency Models: A New Family of Generative Models
      That Achieve High Sample Quality Without Adversarial Training -
      MarkTechPost}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/11ocwgw/textual_inversion_ti_tldr_for_the_lazy_how_to/}{Textual
      Inversion: TI TLDR for the Lazy. How to Make Fake People: Simple
      TI Traning Using 6 Images and very low Settings. Bonus 1: How to
      Make Fake People that Look Like Anything you Want. Bonus 2: Why
      1980s Nightcrawler dont care about your prompts. With Unedited
      Image Samples. : r/StableDiffusion}
    \end{itemize}

    \begin{itemize}
     
    \item
      \href{https://github.com/BelieveDiffusion/tutorials/tree/main/consistent_character_embedding\#readme}{walkthrough
      tutorial for character embedding}
    \end{itemize}
  \item
    \begin{itemize}
     
    \item
      \href{https://www.reddit.com/r/StableDiffusion/comments/11ocwgw/textual_inversion_ti_tldr_for_the_lazy_how_to/}{Textual
      Inversion: TI TLDR for the Lazy. How to Make Fake People: Simple
      TI Traning Using 6 Images and very low Settings. Bonus 1: How to
      Make Fake People that Look Like Anything you Want. Bonus 2: Why
      1980s Nightcrawler dont care about your prompts. With Unedited
      Image Samples. : r/StableDiffusion}
    \end{itemize}
  \item
    \href{https://crsreports.congress.gov/product/pdf/r/r47224}{2
    file\_get\_contents( (other)}
  \item
    \href{https://simonwillison.net/2022/Sep/30/action-transcription/}{A
    tool to run caption extraction against online videos using Whisper
    and GitHub Issues/Actions (other)}
  \item
    \href{https://github.com/carson-katri/dream-textures/pull/409}{Add
    Project Dream Texture operator by carson-katri   Pull Request \#409
      carson-katri/dream-textures   GitHub (other)}

    \begin{itemize}
     
    \item
      other
    \end{itemize}
  \item
    \href{https://github.com/carson-katri/dream-textures/pull/409}{Add
    Project Dream Texture operator by carson-katri   Pull Request \#409
      carson-katri/dream-textures   GitHub (other)}
  \item
    \href{https://dex.aldrin.com/chart/spot/liq_usdc}{Aldrin (other)}

    \begin{itemize}
     
    \item
      The text discusses the ethical implications of machine learning.
      It argues that as machine learning gets better at imitating
      humans, there will be an increasing risk of it being used for
      unethical purposes.
    \end{itemize}
  \item
    Bloomberg.

    \begin{itemize}
     
    \item
      \href{https://www.bloomberg.com/news/articles/2023-02-21/amazon-s-aws-joins-with-ai-startup-hugging-face-as-chatgpt-competition-heats-up}{Bloomberg
      - Are you a robot?:}
    \end{itemize}
  \item
    \href{https://clip-actor.github.io}{CLIP-Actor (other)}

    \begin{itemize}
     
    \item
      Other
    \end{itemize}
  \item
    \href{https://donnerlab.com/}{Connection timed out ,}
  \item
    \href{https://depth-gen.github.io/}{DepthGen (other)}

    \begin{itemize}
     
    \item
      This text discusses using diffusion models for monocular depth
      estimation, which is a technique for measuring the distance to
      objects using just one camera. This could have applications in
      fields like autonomous driving and robotics.
    \end{itemize}
  \item
    \href{https://discord.gg/2xndhbssvv}{Discord (other)}

    \begin{itemize}
     
    \item
      Other. The text is a brief history of the internet, tracing its
      origins back to the 1960s.
    \end{itemize}
  \item
    \href{https://discord.gg/tpd9h8kvbd}{Discord (other)}
  \item
    \href{https://github.com/carson-katri/dream-textures\%7Ccarson-katri/dream-textures\%3Ecarson-katri/dream-textures\%20\%7C\%20dec\%204th\%20\%7C\%20added\%20by\%20github}{dream-textures
    bar{} dec 4th bar{} added by github): failed to open
    stream: (other)}

    \begin{itemize}
     
    \item
    \end{itemize}
  \item
    \href{http://explainpaper.com}{Explainpaper is a service that
    promises to make research papers easy to read. It does this by
    allowing users to upload a paper and then highlights confusing text,
    providing an explanation.}
  \item
    \href{https://hongfz16.github.io/projects/avatarclip.html}{failed to
    open stream: (other)}

    \begin{itemize}
     
    \item
      other
    \end{itemize}
  \item
    \href{https://dex.bonfida.com/\#/market/e14bkbhdwd4eutkwj1oozezesgxmw8lpcps4w5puzzjo}{failed
    to open stream: php\_network\_getaddresses: getaddrinfo failed: Name
    or service not known ,}
  \item
    \href{https://www.d-id.com/chat/}{First of the mobile avatar AI chat
    bots (other)}
  \item
    \href{https://nymag.com/intelligencer/2023/02/gary-gensler-on-meeting-with-sbf-and-his-crypto-crackdown.html}{Gary
    Gensler on Meeting With SBF and His Crypto Crackdown (other)}
  \item
    \href{https://github.com/hayabhay/whisper-ui}{The GitHub repository
    hayabhay/whisper-ui contains a Streamlit UI for
    OpenAIquotesingle s Whisper. The UI allows users to save,
    browse, and search transcriptions. The code is licensed under the
    MIT license.}
  \item
    \href{https://github.com/youwang-kim/clip-actor}{GitHub -
    Youwang-Kim/CLIP-Actor: {[}ECCVquotesingle22{]} Official
    PyTorch Implementation of "CLIP-Actor: Text-Driven Recommendation
    and Stylization for Animating Human Meshes" (other)}
  \item
    https://en.m.wikipedia.org/wiki/Cross-origin\_resource\_sharing
  \item
    https://mobile.twitter.com/BrianRoemmele/status/1640567367418937344
  \item
    https://mobile.twitter.com/heyBarsee/status/1640368028884914178
  \item
    https://open.spotify.com/episode/6z8vib2iyi3kavh67itt9q?si=gq2frm\_stdwk8r\_udt69lw\&utm\_source=copy-link
    2
    file\_get\_contents(https://open.spotify.com/episode/6z8vib2iyi3kavh67itt9q?si=gq2frm\_stdwk8r\_udt69lw\&utm\_source=copy-link):
    failed to open stream: HTTP request failed! HTTP/1.0 500 Internal
    Server Error (other)
  \item
    https://twitter.com/ShitcoinSherpa/status/1625239032518115330?s=20\&t=LZlw1E-cWd1WOSNuSFkrvA
  \item
    https://twitter.com/TomLikesRobots/status/1627073211656732676
  \item
    https:backslash/backslash/github.combackslash/pixegamibackslash/pokemon-card-generator",
  \item
    https:backslash/backslash/m.youtube.combackslash/watch?v=sNcEhR65pw0\&feature=youtu.be",
  \item
    https:backslash/backslash/mobile.twitter.combackslash/FarooqAhmedXbackslash/statusbackslash/1620925310379368448",
  \item
    https:backslash/backslash/ncase.mebackslash/trustbackslash/",
  \item
    https:backslash/backslash/twitter.combackslash/udnaanbackslash/statusbackslash/1619873609136181251",
  \item
    https:backslash/backslash/www.reddit.combackslash/rbackslash/StableDiffusionbackslash/commentsbackslash/10ir9bfbackslash/my\_mix\_for\_landscapesbackslash/",
  \item
    https:backslash/backslash/www.reddit.combackslash/rbackslash/virtualrealitybackslash/commentsbackslash/10l23a3backslash/beta\_control\_obs\_in\_vrbackslash/",
  \item
    Jeremy Bailenson talks about 1,000,000 Walmart employees training
    with VR, presence, and the VR backslash"empathy
    machinebackslash" - The Ghost Howls
    https://skarredghost.com/2022/09/01/jeremy-bailenson-interview-vr/
    (other)
  \item
    place\_holder\_topic

    \begin{itemize}
     
    \item
      https://mobile.twitter.com/clamstech/status/1640810071725842432
    \end{itemize}
  \item
    \href{https://www.reddit.com/r/virtualreality/comments/u4ahwu/horizon_worlds_coming_to_smartphones_web_probably/}{Horizon
    worlds coming to smartphones?}
  \item
    \href{https://www.reddit.com/r/CryptoCurrency/comments/10wx51p/the_current_list_of_cbdcs_in_development_around/}{CBDCs
    in development around the world}
  \item
    \href{https://medium.com/@gladia.io/gladia-alpha-launch-redefining-what-s-possible-with-speech-to-text-ai-686dd4312a86}{Redefining
    What's Possible with Speech-to-Text AI bar{} by Gladia.io
    bar{} Feb, 2023 bar{} Medium (other)}
  \item
    \href{https://m.youtube.com/watch?v=L_Guz73e6fw\&feature=youtu.be}{Sam
    Altman: OpenAI CEO on GPT-4, ChatGPT, and the Future of AI
    bar{} Lex Fridman Podcast \#367: Sam Altman is the CEO of
    OpenAI, the company behind GPT-4, ChatGPT, DALL-E, Codex, and many
    other state-of-the-art AI technologies. Please support this
    podca...}
  \item
    Saturday -
    10:15backslash nhttps://events.sansar.com/events/PJ-Mac-3293/day-2-\/-intermodal-year-one/1fdcec68
    (other)
  \item
    Saturday -
    10:15backslash nhttps://events.sansar.com/events/PJ-Mac-3293/day-2-\/-intermodal-year-one/1fdcec68
    (other)
  \item
    \href{https://arstechnica.com/information-technology/2023/02/sci-fi-becomes-real-as-renowned-magazine-closes-submissions-due-to-ai-writers}{Sci-fi
    becomes real as renowned magazine closes submissions due to AI
    writers bar{} Ars Technica (other)}

    \begin{itemize}
     
    \item
      other
    \end{itemize}
  \item
    scrapeghost.

    \begin{itemize}
     
    \item
      \href{https://jamesturk.github.io/scrapeghost/}{scrapeghost:}

      \begin{itemize}
       
      \item
        The Scrapeghost library allows users to scrape structured data
        from HTML without writing page-specific code. The library is
        still experimental and has some limitations, but it provides a
        quick and easy way to gather data from websites.
      \end{itemize}
    \end{itemize}
  \item
    \href{https://youtu.be/zLnhg9kir3Q}{Stephen Wolfram Answers Live
    Questions About ChatGPT: Stephen Wolfram hosts a live and unscripted
    Ask Me Anything about the history of science and technology for all
    ages. Find the playlist of Q\&Aquotesingle s here: https:...}
  \item
    Tencent Cloud.

    \begin{itemize}
     
    \item
      \href{https://www.tencentcloud.com/dynamic/news-details/100437?lang=en\&pg=}{Tencent
      Cloud:}
    \end{itemize}
  \item
    \href{https://www.army.mil/standto/archive/2018/03/26/}{U.S. Army
    STAND-TO! bar{} Synthetic Training Environment (other)}

    \begin{itemize}
     
    \item
      This text contains a menu for a website called "Nav-army-s." There
      is no good fit for this text in any of the given categories.
    \end{itemize}
  \item
    \href{https://huggingface.co/spaces/nagasaiabhinay/unclip_image_interpolation_demo}{UnCLIP
    Image Interpolation Demo - a Hugging Face Space by NagaSaiAbhinay
    (other)}

    \begin{itemize}
     
    \item
      Other. This text does not seem to fit well into any of the given
      topics.
    \end{itemize}
  \item
    Understanding Deep Learning

    \begin{itemize}
     
    \item
      \href{https://udlbook.github.io/udlbook/}{This book provides an
      overview of deep learning, including supervised and unsupervised
      learning, loss functions, training models, gradient descent, and
      measuring performance. It also covers convolutional and recurrent
      neural networks, as well as generative adversarial networks and
      reinforcement learning.}
    \end{itemize}
  \item
    Unreal Engine 5 Editor Utility widgets

    \begin{itemize}
     
    \item
      \href{https://github.com/TREE-Ind/UnrealGPT}{This repository
      contains a collection of Unreal Engine 5 Editor Utility widgets
      powered by GPT3/4.}
    \item
      \href{https://www.youtube.com/watch?v=FQgsQLodcZM}{Unreal Engine
      5.2 - Experimental Pixel Streaming to WebXR: NOT PRODUCTION-READY
      or even supported directly Epic or even technically WebXR... but
      it sure does feel a lot like it.}
    \end{itemize}
  \item
    \href{http://WavTool.com}{WavTool:}
  \item
    web three aid memoire for
    mebackslash nhttps://twitter.com/PastryEth/status/1529130859814600705
    (other)
  \item
    web three aid memoire for
    mebackslash nhttps://twitter.com/PastryEth/status/1529130859814600705
    (other)
  \item
    \href{https://hackmd.io/@xr/monetization}{WebXR Monetization -
    HackMD (other)}

    \begin{itemize}
     
    \item
      Other
    \end{itemize}
  \item
    \href{https://webdevlaw.uk/2022/07/11/your-compliance-obligations-under-the-uks-online-safety-bill/}{Your
    compliance obligations under the UK's Online Safety Bill; or,
    welcome to hell -- Hi, Iquotesingle m Heather Burns (other)}
  \item
    \href{https://webdevlaw.uk/2022/07/11/your-compliance-obligations-under-the-uks-online-safety-bill/}{Your
    compliance obligations under the UK's Online Safety Bill; or,
    welcome to hell -- Hi, Iquotesingle m Heather Burns (other)}
  \item
    \href{https://www.bloomberg.com/news/articles/2023-02-21/amazon-s-aws-joins-with-ai-startup-hugging-face-as-chatgpt-competition-heats-up}{Bloomberg
    - Are you a robot?:}
  \item
    \href{https://www.reddit.com/r/CryptoCurrency/comments/10wx51p/the_current_list_of_cbdcs_in_development_around/}{Reddit
    - Dive into anything:}
  \item
    \href{https://www.tencentcloud.com/dynamic/news-details/100437?lang=en\&pg=}{Tencent
    Cloud:}
  \item
    \href{https://www.linkedin.com/posts/activity-7046131519802757120-uUEf?utm_source=share\&utm_medium=member_android}{Sign
    Up bar{} LinkedIn: 500 million+ members bar{} Manage your
    professional identity. Build and engage with your professional
    network. Access knowledge, insights and opportunities.}

    \begin{itemize}
     
    \item
      This text provides information on the lazyloader, tracking, and
      impressionTracking variables in the LinkedIn codebase. These
      variables are used to manage Promises and improve performance.
    \end{itemize}
  \item
    https://twitter.com/TomLikesRobots/status/1628104009146826763?s=20
  \item
    https://twitter.com/ShitcoinSherpa/status/1625239032518115330?s=20\&t=LZlw1E-cWd1WOSNuSFkrvA
  \item
    https://twitter.com/TomLikesRobots/status/1627073211656732676
  \item
    \href{https://twitter.com/daniel_eckler/status/1564601398284664832?s=20\&t=79zgNMrzbD89cQto2u5j-Q}{ML
    verticals twitter thread}
  \item
    \href{https://github.com/AUTOMATIC1111/stable-diffusion-webui/wiki/Developing-extensions}{Automatic1111
    robot plugin}
  \item
    2D to blender 3D workflow.
  \item
    \href{https://upscayl.github.io/}{Free opens source image upscaler}
  \item
    \href{https://txt.cohere.ai/sentence-word-embeddings/}{About
    sentence embedding}
  \item
    \href{https://laion.ai/blog/giant-openclip/}{Image giant openclip
    descriptions from images}
  \item
    \href{https://metavert.substack.com/p/the-generative-ai-canon}{the
    generative AI canon substack roundup}
  \item
    \href{https://www.sequoiacap.com/article/generative-ai-a-creative-new-world/}{sequoia
    capital generative AI landscape}
  \item
    \href{https://www.linkedin.com/posts/zainkahn_1000-ai-tools-were-released-in-march-activity-7048285306101358592-4wAA?utm_source=share\&utm_medium=member_android}{Zain
    Kahn on LinkedIn: 1,000+ AI tools were released in March.}
  \item
    \href{https://www.linkedin.com/posts/venu-victor-aa7ab865_houdini-ai-python-activity-7030460619195629568--Sx9?}{Venu
    Victor on LinkedIn: \#houdini \#ai \#python \#chatgpt: Using GPT
    in~\#houdini~\#ai~\#python~\#chatgpt FxGPTv02 My script analyses the
    user input and asks the question in such a way that answers are
    always to the dot.\ldots{}}

    \begin{itemize}
     
    \item
      The text describes a script which can be used to automatically
      generate questions and answers in Houdini, using AI and machine
      learning. The script is designed to be used in chat applications,
      and can be customized to ask specific questions or provide general
      information.
    \end{itemize}
  \item
    \href{http://hystax.com}{The text describes the benefits of using
    the FinOps and MLOps open source platforms. These platforms allow
    for better management of financial operations and machine learning
    operations, respectively.}
  \item
    \href{https://gemm.ai/learning-to-grow-machine-learning-models/}{Can
    we improve the efficiency of these training methods, so we can still
    get good models in less time and for less money? We propose to do
    this by leveraging smaller language models that have previously been
    trained,}
  \item
    \href{https://www.linkedin.com/posts/eric-vyacheslav-156273169_big-news-meta-just-released-segment-anything-activity-7049409700370554880-tStk?utm_source=share\&utm_medium=member_android}{Segment
    Anything, which can "cut out" any object in any image or video with
    a single click. The model is designed and trained to be promptable,
    so it can transfer zero-shot to new image distributions and tasks.}
  \item
    \href{http://github.com/baaivision/Painter}{This repository contains
    code for the Painter and SegGPT models from the BAAI Vision
    Foundation. These models are designed for in-context visual
    learning, and can be used to segment images and generate
    descriptions of them.}
  \item
    \href{https://buff.ly/3KD0Zns}{The text presents SegGPT, a
    generalist model for segmenting everything in context. The model is
    trained to unify various segmentation tasks into a generalist
    in-context learning framework, and is evaluated on a broad range of
    tasks, including few-shot semantic segmentation, video object
    segmentation, semantic segmentation, and panoptic segmentation.
    Results show strong capabilities in segmenting in-domain and
    out-of-domain targets, either qualitatively or quantitatively.}
  \item
    \href{https://www.linkedin.com/posts/guohao-li-9a573b136_camel-chatbot-demo-activity-7051390760327225344-8D2A?utm_source=share\&utm_medium=member_android}{The
    text describes the Camel Chatbot, a machine learning model that has
    been trained using data from the AI Society and Code datasets. The
    chatbot is designed to improve the coding ability of users. The text
    includes a link to a demo of the chatbot in action.}
  \item
    \href{https://github.com/RosettaCommons/RFdiffusion}{RFdiffusion is
    a codebase for running diffusion simulations. It is designed to work
    with the SE3-transformer library and to be used in conjunction with
    the PPI scaffold examples. Basic execution of the diffusion script
    is straightforward, and the inpaint\_seq flag can be used to control
    the output. Partial diffusion is also possible, and the binder
    design can be used to constrain the diffusion.}
  \item
    \href{https://wolfr.am/1cCK87Nms}{Daily Study Group: The Wolfram
    Plugin for ChatGPT: Learn about the Wolfram ChatGPT plugin for
    access to powerful computation, curated knowledge, real-time data,
    visualization and even code generation.}
  \item
    \href{https://twitter.com/justLV/status/1637876167763202053}{Fast
    mobile voice based chatbot}
  \end{itemize}
\item
  Assisted creativity
\item
  human stuff

  \begin{itemize}
  \item
    \href{https://dl.acm.org/doi/abs/10.1145/3528233.3530740}{Volumetric
    primitives (MVP) avatar representation of Lombardi et al.
    {[}2021{]}.}
  \item
    \href{https://arxiv.org/abs/2205.06254}{Single shot vertex fitting}
  \item
    \href{https://meshcapade.com/}{Meshcapade virtual humans}
  \item
    \href{https://share.synthesia.io/a5a12c73-09cb-4455-b007-147ae4b1effb}{AI
    video actor}
  \item
    \href{https://ofa-sys.github.io/MoFusion/}{text to human motion}
  \item
    \href{https://talkshow.is.tue.mpg.de/}{text to speech to simulated
    speaking movement}
  \item
    \href{https://www.linkedin.com/posts/reneschulte_nerf-deeplearning-metaverse-activity-7010898662465617921-56P_?utm_source=share\&utm_medium=member_desktop}{nerf
    avatars}
  \item
    \href{https://twitter.com/IntuitMachine/status/1608690077139599360}{chatgpt
    to avatar}
  \item
    \href{https://www.mmlab-ntu.com/project/vtoonify/}{toonify code and
    model}
  \item
    \href{https://github.com/Meta-Portrait/MetaPortrait}{Talking head
    modifier}
  \item
    \href{https://www.d-id.com/}{AI face studio}
  \item
    MoveAI
  \item
    \href{http://arxiv.org/pdf/2301.00250.pdf}{wifi based pose
    estimation}
  \item
    \href{https://3d-avatar-diffusion.microsoft.com/?utm_campaign=AI\%20Art\%20Weekly\&utm_medium=email\&utm_source=Revue\%20newsletter\#/}{Microsoft
    sculpted avatars}
  \item
    \href{https://80.lv/articles/ziva-dynamics-announces-a-new-ml-trained-facial-rigging-service/}{ML
    realtime UE facial expresssions}
  \item
    \href{https://studios.disneyresearch.com/2022/11/30/production-ready-face-re-aging-for-visual-effects/}{Disney
    face aging}
  \item
    \href{https://talkshow.is.tue.mpg.de/}{Gestures from speech}
  \item
    \href{https://volucap.com/}{Volucap volumentric deep fakes}
  \item
    \href{https://www.flawlessai.com/}{FlawlessAI cloud facial plus
    language translattion}
  \item
    \href{https://masterpiecestudio.com/blog/announcing-generative-animations}{language
    to animated character}
  \item
    \href{https://github.com/JimWest/MeFaMo}{instant phone to unreal
    face opensource}
  \item
    \href{https://www.youtube.com/watch?v=zgj24gTjQtY}{consistent pose
    and angles in stable diffusion}
  \item
    \href{https://www.youtube.com/watch?v=XWJGmNW15A4}{Generating
    Consistent Characters using Stable Diffusion}
  \item
    \href{https://www.youtube.com/watch?v=Ig1S2guCfKM}{consistent
    characters}
  \item
    \href{https://www.youtube.com/watch?v=-iwPVUzAWzk}{character
    turnarounds SD}
  \item
    \href{https://github.com/vye16/slahmr}{Decoupling humans from
    backgrounds}
  \item
    Hybrid ML humans for mobile
  \item
    \hypertarget{message-content-1079000811318812742}{}
    You can very plausibly do this with controlnet and openpose type
    stuff and get a smoother 2d experience on the screen
  \item
    \hypertarget{message-content-1079000989610283130}{}
    effectively server side work though so becomes harder for the
    modding side
  \item
    \hypertarget{message-content-1079001213984591922}{}
    the advantage is therequotesingle s a ready baked mod community
    for the PC engine interface (people who will really want to do this
    stuff)
  \item
    \hypertarget{message-content-1079001578956132422}{}
    youquotesingle d have two products running on one
    infrastrature. Object, scene, openpose layer (server side) driven by
    the AI. Server side render layer pushing interactive video to
    mobile, and a direct object, scene, openpose API interface on the
    same payment plans for the ML modding community
  \item
    \hypertarget{message-content-1079001659209945199}{}
    i think that could be pretty elegant and it gives you MUCH faster
    iteration loops
  \item
    plus itquotesingle s pure honey for investors because it
    sidesteps the internal doubts they have about 3D on devices
  \item
    \href{https://github.com/Skype-line/X-Avatar}{Expressive human
    avatars}
  \item
    \href{https://moygcc.github.io/vid2avatar/}{Vid2Avatar: 3D Avatar
    Reconstruction from Videos in the Wild via Self-supervised Scene
    Decomposition (other)}
  \item
    \href{https://flex.cs.columbia.edu/}{FLEX: Full-Body Grasping
    Without Full-Body Grasps - Columbia Computer Vision Lab (other)}
  \item
    \href{https://machinelearning.apple.com/research/neural-3d-relightable}{Apple
    facial relighting}
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/12dxue5/controlnet_face_model_for_sd_15/}{Controlnet
    face model for SD1.5}
  \end{itemize}
\item
  Unsorted links

  \begin{itemize}
   
  \item
    \href{http://chartgpt.dev}{This tool converts text into beautiful
    charts. It is made with React, Next.js, OpenAI and Tailwind CSS.}
  \item
    \href{https://github.com/chainyo/picaisso}{PicAIsso is an
    open-source StableDiffusion implementation for generating AI art
    using an API and a Discord Bot.}
  \item
    \href{https://darkfutura.substack.com/p/record-labels-panic-as-ai-generated}{Record
    Labels Panic as A.I. Generated Song Becomes Hit Single: Welcome to
    the new world.}
  \item
    \href{https://github.com/Mikubill/sd-webui-controlnet/pull/903}{This
    is a super high-quality sampling for image resizing and high-res
    resizing. It keep segmentation maps as segmentation maps with
    arbitary resizing, it keep canny maps as canny maps with arbitary
    resizing, it keep mlsd maps as mlsd maps with arbitary resizing, and
    it keep scribble maps as scribble maps with arbitary resizing. Also,
    now if users use high-res fix, the both two control maps in low res
    and high res will be visualized so that users know the two passes.}
  \item
    \href{https://jonbarron.info/zipnerf/}{Zip-NeRF: This paper presents
    a new technique for training neural radiance fields, which combines
    ideas from rendering and signal processing to yield better results
    than either previous technique. The new technique is called
    Zip-NeRF, and it is faster and more accurate than the previous
    techniques.}
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/12od46u/360_vr_image_read_comment/}{360
    drobe style aerial image generative art prompt}
  \item
    Ultimate Guide to Upscale Images with AI in Stable Diffusion
    https://onceuponanalgorithm.org/ultimate-guide-to-upscale-images-with-ai-in-stable-diffusion/
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/12cqb7k/i_suddenly_remembered_the_crazy_talk_app_it_is/}{Crazy
    Talk app! It is cheap, has an editor for the faces of the characters
    (even from a photo) and fine-tuning emotions for them. Works well
    with Control Net.}
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/12nzrtl/hdr_photography_style_landscapesseascapes/}{HDR
    landscape model}
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/12nd60i/turn_a_group_photo_into_a_digital_painting_with/}{Workflow for turning a group photo into a digital art}
  \end{itemize}
\item
  Music and audio

  \begin{itemize}
  \item
    \href{https://storage.googleapis.com/music-synthesis-with-spectrogram-diffusion/index.html}{Stable
    diffusion MIDI}
  \item
    \href{https://github.com/teticio/audio-diffusion}{Trainable github}
  \item
    \href{https://app.prodia.com/\#/}{Propia instant jukebox}
  \item
    \href{https://www.riffusion.com/about}{SD for music}
  \item
    \href{https://www.musicradar.com/news/audiocipher-word-midi-music-generator-creative-block}{word
    to midi}
  \item
    \href{https://www.harmonai.org/}{HarmonAI}
  \item
    \href{https://github.com/riffusion/riffusion-app}{Riffusion}
  \item
    \href{https://www.beatoven.ai/}{Beatoven: Create unique royalty-free music.}
  \item
    \href{https://krisp.ai/}{Krise: Removes background voices, noises
    and echo during calls.}
  \item
    \href{https://google-research.github.io/seanet/musiclm/examples/}{Google
    MusicLM}

    \begin{itemize}
     
    \item
      \href{https://techcrunch.com/2023/01/27/google-created-an-ai-that-can-generate-music-from-text-descriptions-but-wont-release-it/}{techcruch
      explaining why it wonquotesingle t be released}
    \end{itemize}
  \item
    \href{https://text-to-audio.github.io/}{Text2audio}
  \item
    \href{https://github.com/libAudioFlux/audioFlux}{The audioFlux
    library is a tool for audio and music analysis, featuring extraction
    capabilities. It is open source and released under the MIT license.}
  \item
    \href{https://www-engadget-com.cdn.ampproject.org/c/s/www.engadget.com/amp/grimes-invites-ai-artists-to-use-her-voice-promising-50-percent-royalty-split-165659578.html}{Grimes
    invites royalty split with anyone using her voice}
  \end{itemize}
\item
  3d geometry

  \begin{itemize}
   
  \item
    \href{https://samsunglabs.github.io/rome/}{geom head from single
    shot}
  \item
    \href{https://www.youtube.com/watch?v=uboj01Gfy1A}{Microsoft AI
    faces}
  \item
    \href{https://replicate.com/yoyo-nb/thin-plate-spline-motion-model}{Face
    to face mapping}
  \item
    \href{https://katjaschwarz.github.io/voxgraf/}{Image to voxel faces}
  \item
    3D model from text
  \item
    \href{https://nv-tlabs.github.io/GET3D/}{GET3D}
  \item
    \href{https://github.com/openai/point-e}{openai point-e}
  \item
    \href{https://ajayj.com/dreamfields}{Dream3D}
  \item
    \href{https://nv-tlabs.github.io/GET3D/}{GET3D}
  \item
    \href{https://nv-tlabs.github.io/LION/}{LION instant 3D textured
    geom}
  \item
    \href{https://katjaschwarz.github.io/voxgraf/}{Image to voxel faces}
  \item
    \href{https://github.com/autodeskailab/clip-forge}{Clipforge}
  \item
    \href{https://paperswithcode.com/paper/text-to-mesh-without-3d-supervision-using}{clip
    mesh}
  \item
    \href{https://github.com/carson-katri/dream-textures/pull/409}{Geom
    texturing from prompts in blender}
  \item
    \href{https://twitter.com/TomLikesRobots/status/1603884188326940674}{blender
    3d from 2d twitter thread}
  \item
    \href{https://github.com/zoomin-lee/scene-scale-diffusion}{composite
    scene generation}
  \item
    \href{https://threedle.github.io/3DHighlighter/}{3D Highlighter:
    Localizing Regions on 3D Shapes via Text Descriptions}
  \item
    \href{https://nv-tlabs.github.io/vqad/}{Variable bitrate neural
    field objects}
  \item
    \href{https://ofa-sys.github.io/MoFusion/}{Text to human avatar
    motion}
  \item
    \href{https://zju3dv.github.io/onepose_plus_plus/}{Oneshot post
    estimation for AR}
  \item
    \href{https://captures.lumalabs.ai/imagine}{Luma text to 3D}
  \item
    \href{https://echoesofsomewhere.com/2023/01/25/modeling-a-robot-with-some-added-difficulty/}{Game
    assets hybrid workflow}
  \item
    \href{https://monstermash.zone/}{monstermash, animated creatures
    from 2d sketch}
  \item
    \href{https://www.reddit.com/r/virtualreality/comments/xvy5dc/3d_generation_from_a_single_image/}{3D
    generation from a single image : r/virtualreality}
  \item
    \href{https://github.com/gd3kr/BlenderGPT}{blender plugin}
  \item
    \href{https://make-it-3d.github.io/}{Make-It-3D: High-Fidelity 3D
    Creation from A Single Image with Diffusion Prior:}
  \item
    \href{https://github.com/threedle/3dhighlighter}{GitHub -
    threedle/3DHighlighter: Localizing Regions on 3D Shapes via Text
    Descriptions (other)}
  \item
    "Vox-E: Text-guided Voxel Editing of 3D Objects."
  \item
    \href{https://dreamfusion3d.github.io/}{DreamFusion: Text-to-3D
    using 2D Diffusion (other)}
  \item
    \href{https://lukashoel.github.io/text-to-room/}{Text2Room:
    Extracting Textured 3D Meshes from 2D Text-to-Image Models:}
  \item
    \href{https://bennyguo.github.io/vmesh/}{VMesh: Hybrid Volume-Mesh
    Representation for Efficient View Synthesis :}
  \item
    \href{https://lv3d.github.io/urbanGIRAFFE/?trk=public_post_comment-text}{City
    scenes from geom?}
  \item
    \href{https://jeffreyxiang.github.io/ivid/}{3d aware image to
    object}
  \item
    "text-to-3D generation."

    \begin{itemize}
     
    \item
      \href{https://ku-cvlab.github.io/3DFuse/}{Let 2D Diffusion Model
      Know 3D-Consistency for Robust Text-to-3D Generation:}
    \end{itemize}
  \item
    \href{http://weiyuli.xyz/Sin3DGen/}{Patch based 3D natural scenes}
  \item
    \href{https://arxiv.org/abs/2212.08751}{Complex prompt to 3D}
  \item
    \href{https://www.youtube.com/watch?v=t9zzcRsf0IA}{Nice blender to
    360 geometry tutorial workflow}
  \end{itemize}
\item
  Text and bots

  \begin{itemize}
   
  \item
    \href{https://news.artnet.com/art-world/chatgpt-art-theory-hal-foster-2263711}{lying
    lying heart of chatgpt}
  \item
    \href{https://simonwillison.net/2022/Sep/30/action-transcription/}{Caption
    extraction}
  \item
    \href{https://arxiv.org/abs/2212.14034}{cramming language model in a
    day}
  \item
    \href{https://nlpcloud.com/build-gpt-j-gpt-neox-discord-chatbot-with-nlpcloud.html}{Discord
    bot tutorial}
  \item
    \href{https://techcrunch.com/2022/01/12/the-metaverse-will-be-filled-with-elves/}{Elves
    (bots) techcrunch article}
  \item
    \href{https://www.linkedin.com/feed/update/urn:li:activity:7005874144621809666/}{GPT-3
    resources}
  \item
    \href{https://80-lv.cdn.ampproject.org/c/s/80.lv/articles/step-by-step-instruction-on-unreal-s-blueprints-generated-with-chatgpt/?amp=1}{Unreal
    blueprint chatgpt}
  \item
    \href{https://www.newscientist.com/article/2350655-openai-is-developing-a-watermark-to-identify-work-from-its-gpt-text-ai/}{DRM
    fingerprinting}
  \item
    \href{https://github.com/LAION-AI/Open-Assistant}{OpenChatGPT}
  \item
    \href{https://www.gptoverflow.link/question/1519492600837443584/chatgpt-political-compass}{political
    compass}
  \item
    \href{https://www.atomic14.com/2022/12/05/using-chatgpt-as-a-co-founder.html}{Using
    ChatGPT as a founder}
  \item
    \href{https://docs.google.com/forms/d/e/1FAIpQLScwuQEWBkxsNftEkvUgFx2Ov7pKcrOx8IUlZ241lvet7ziXCQ/viewform?fbzx=-7085331511137611549}{chatgpt
    waitlist for pro}
  \item
    \href{https://replicate.com/methexis-inc\#}{Img2Prompt}
  \item
    \href{https://support.mem.ai/article/97-mem-x-smart-write-and-edit\#funny}{Mem.ai
    writing support}
  \item
    \href{https://thundercontent.com/features}{Thundercontent: Generates
    all types of written}
  \item
    \href{https://www.askcorpora.com/dashboard}{Corpora PDF}
  \item
    \href{https://www.contextable.ai/}{contexable}
  \item
    \href{https://www.reddit.com/r/ChatGPT/comments/10tevu1/new_jailbreak_proudly_unveiling_the_tried_and/}{New
    jailbreak! Proudly unveiling the tried and tested DAN 5.0 - it
    actually works - Returning to DAN, and assessing its limitations and
    capabilities. : r/ChatGPT}
  \item
    \href{https://arxiv.org/abs/2210.03629}{Paper on feedback React}
  \item
    \href{https://github.com/OpenMindClub/awesome-chatgpt}{chatgpt
    currated links}
  \item
    \href{https://github.com/KoboldAI/KoboldAI-Client}{KoboldAI assisted
    writing}
  \item
    Generative storytelling
  \item
    \href{https://beta.tome.app/}{The AI-powered storytelling format:
    Unlock your best work with Tomequotesingle s AI-powered
    storytelling format. Type in a prompt and generate entire narratives
    from scratch within seconds, supported by GPT-3 and AI-generated
    images from DALL E 2.}
  \item
    \href{https://deepmind.github.io/dramatron/}{Dramatron (other)}
  \item
    This demo and arxiv paper are for a tool called Dramatron that uses
    machine learning to help with writing scripts.
  \item
    \href{https://github.com/Project-Akiko}{Making an Open Source Twitch
    VTuber with TTS and Language Model processing, and creating a
    universal Chat Platform for LLMs like Pygmalion, LLaMA and others.}
  \item
    \href{https://github.com/RafalWilinski/telegram-chatgpt-concierge-bot}{telegram
    bot concierge}
  \item
    \href{https://github.com/hc20k/LLMChat}{discord LLM bot with voice}
  \item
    \href{https://github.com/yoheinakajima/babyagi}{BabyAGI task bot}
  \item
    \href{https://github.com/deep-diver/LLM-As-Chatbot}{Alpaca-lora-serve
    simple interface for chat}
  \item
    \href{https://docs.google.com/spreadsheets/d/1UsbivogLMrQbBA-Fk0ESRGTrvCsknBUieSykfWn6D9Q/edit\#gid=0}{Performance
    spreadsheets}
  \item
    \href{https://huggingface.co/stabilityai/stablelm-tuned-alpha-7b}{StabilityLM
    tuned model}
  \item
    \href{https://github.com/Wladastic/Auto-GPT-Telegram-Plugin}{Telegram
    bot AutoGPT integration}
  \end{itemize}
\item
  Voice
\item
  \href{https://www.youtube.com/watch?v=nwPaRSlDSaY}{Brillbits OpenAI
  whisper demo with mic}
\item
  \href{https://github.com/openai/whisper}{OpenAI whisper local deploy}
\item
  \href{https://github.com/davabase/transcriber_app/}{realtime
  transciber}
\item
  \href{https://github.com/ggerganov/whisper.cpp}{high performance CPP}
\item
  \href{https://cleanvoice.ai/}{Cleanvoice audio denoise}
\item
  \href{https://voice.ai/}{Cloud voice change app}
\item
  \href{https://github.com/neonbjb/tortoise-tts}{downloadable voice
  generation systems}
\item
  \href{https://txt.cohere.ai/introducing-sandbox-coheres-experimental-open-source-initiative/}{Language
  AI open libraries}
\item
  \href{https://huggingface.co/spaces/JavaFXpert/Chat-GPT-LangChain}{Language
  practice}
\item
  \href{https://mugen-org.github.io/}{MUGEN multi modal from facebook}
\item
  \href{https://atosystem.github.io/blogs/speechclip}{Oneshot speach to
  text}
\item
  \href{https://podcastle.ai/}{Record and cleanup pro audio with
  commodity hardware}
\item
  \href{https://variety.com/2022/digital/news/james-earl-jones-darth-vader-retiring-star-wars-ai-1235382827/}{Respeecher}
\item
  \href{https://voice.ai/}{Voice AI voices}
\item
  \href{https://the-decoder.com/developer-combines-stable-diffusion-whisper-and-gpt-3-for-a-futuristic-design-assistant/}{Voice
  controlled assisted creation}
\item
  \href{https://blog.lopp.net/open-source-transcription-software-comparisons/}{Voice
  to text, Lopp}
\item
  \href{https://github.com/modal-labs/modal-examples/tree/main/misc/whisper_pod_transcriber}{whisper
  transcriber}
\item
  \href{https://huggingface.co/spaces/JavaFXpert/Chat-GPT-LangChain}{Wolfram
  alpha voice chatbot integration}
\item
  \href{https://valle-demo.github.io/}{Microsoft Vall-E voice synthesis}
\item
  \href{https://app.uberduck.ai/}{Uberduck text to speech (plus own
  voice)}
\item
  \href{https://beta.elevenlabs.io/}{Eleven labs language and text to
  speech}
\item
  \href{https://uberduck.ai/}{Uberduck open source text to speech}
\item
  \href{https://numenvoice.com}{numen voice control system in linux}
\item
  \href{https://www.youtube.com/watch?v=DnF4WzM5LPU}{Inworld (steam game
  plugin AI system) for voice chat and answer}
\item
  \href{https://github.com/suno-ai/bark}{Bark text to speech from google
  labs}
\item
  \href{https://www.youtube.com/watch?v=TGZV831VTpc}{VoiceVox engine}
\item
  \href{https://www.futurepedia.io/}{Compendium of tools}
\item
  images
\item
  \href{https://sdtools.org/}{Stability specific tools}
\item
  Arible Prompt Database https://www.arible.co/prompts
\item
  \href{https://civitai.com/models/22530}{{[}Guide{]} Make your own
  Loras, easy and free bar{} Stable Diffusion Other bar{}
  Civitai: You donquotesingle t need to download anything, this is
  a guide with online tools. Click "Show more" below.   Preamble Even if
  you donquotesingle t know where to start o...}
\item
  \href{https://github.com/bmaltais/kohya_ss}{Lora training interface
  for windows}
\item
  \href{https://civitai.com/models/8392/refined}{Refined model}
\item
  \href{https://civitai.com/models/5952}{Experience bar{} Stable
  Diffusion Checkpoint bar{} Civitai: Check the versions bellow
  With the release of Experience v7.0, there is now a second version you
  may be interested in; Realistic Experience Version...}
\item
  \href{https://substack.com/profile/110613456-followfoxai}{Fine tuning
  with captioning and other fine tuning tricks, followfox}
\item
  \href{https://huggingface.co/datasets/Nerfgun3/bad_prompt}{Negative
  embedding textual inversion for hands etc}
\item
  \href{https://github.com/kpthedev/ez-text2video}{GitHub -
  kpthedev/ez-text2video: Easily run text-to-video diffusion with
  customized video length, fps, and dimensions on 4GB video cards, as
  well as on CPU.: Easily run text-to-video diffusion with customized
  video length, fps, and dimensions on 4GB video cards, as well as on
  CPU. - GitHub - kpthedev/ez-text2video: Easily run text-to-video
  diffusion wit...}
\item
  \href{https://github.com/xXAdonesXx/NodeGPT}{This repository contains
  a ComfyUI Extension for Automated Text Generation. The extension
  provides nodes which can be used to automate the text generation
  process. The goal is to build a node-based Automated Text Generation
  AGI. This extension should ultimately combine all of the features of
  the existing text generation tools into one tool.}
\item
  \href{https://www.reddit.com/r/MachineLearning/comments/12ehcez/r_texttoimage_diffusion_models_in_generative_ai_a/}{{[}R{]}
  Text-to-image Diffusion Models in Generative AI: A Survey :
  r/MachineLearning}
\item
  \href{https://github.com/BelieveDiffusion/tutorials/discussions/3}{Tutorial:
  Creating a Consistent Character as a Textual Inversion Embedding}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12hkdy8/sd_webui_segment_everything/}{Segment
  anything webui}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12lg8mn/override_more_experiments_overriding_the_original/}{Overriding
  iphone footage with SD characters using controlnet}
\item
  \href{https://github.com/mattdesl/gifenc}{Colour palette extraction}
\item
  \href{https://arxiv.org/abs/2210.09276}{Text based real time image
  manipulation}
\item
  \href{https://sketch-guided-diffusion.github.io/}{Sketch guided text
  to image inference}
\item
  \href{https://www.youtube.com/watch?v=lHcPtbZ0Mnc}{Google prompt to
  prompt image remodeller}

  \begin{itemize}
   
  \item
    \href{https://github.com/google/prompt-to-prompt}{github}
  \end{itemize}
\item
  \href{https://replicate.com/methexis-inc\#}{Img2Prompt}
\item
  \href{https://deepimagination.cc/eDiffi/}{eDiffi nvidia text to image}
\item
  \href{https://laion.ai/blog/laion-coco/}{Image to caption}
\item
  \href{https://github.com/Sanster/lama-cleaner}{lama image cleanup}
\item
  \href{https://upscale.wiki/wiki/Model_Database}{upscalers}

  \begin{itemize}
   
  \item
    \href{https://github.com/upscayl/upscayl}{upscayl}
  \end{itemize}
\item
  \href{https://www.infoq.com/news/2023/01/google-muse-text-to-image/}{Google
  Muse}
\item
  \href{https://flair.ai/}{Flair generate photo shoots of products}
\item
  \href{https://illustroke.com/}{Vector graphics from text}
\item
  \href{https://stockimg.ai/}{Simple stock image generator}
\item
  \href{https://www.patterned.ai/}{Patterned: Generates royalty-free
  patterns.}
\item
  \href{https://cleanup.pictures/}{Cleanup.picture: Removes objects,
  defects, people or text from your images.}
\item
  \href{https://looka.com/}{Looka: Generates brand names and logos.}
\item
  \href{https://github.com/pharmapsychotic/clip-interrogator}{CLIP
  interrogator and prompt engineering colab}
\item
  \href{https://magniv.notion.site/PromptLayer-Docs-db0e6f50cacf4564a6d09824ba17a629}{Prompt
  management engine (local and cloud) (promptlayer)}
\item
  \href{https://github.com/damo-vilab/composer}{Composer stable
  diffusion TYPE model}
\item
  \href{https://multidiffusion.github.io/}{Multi-diffusion panoramas}
\item
  \href{https://www.usegalileo.ai/}{UX design AI}
\item
  \href{http://www.cs.cmu.edu/~pix2pix3D/}{pix2pix-3D: 3D-aware
  Conditional Image Synthesis}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11mzxyu/huggingface_demo_for_elite_new_finetuning/}{HuggingFace
  Demo for /ELITE: new fine-tuning technique that can be trained in less
  than a second/ now available : r/StableDiffusion}
\item
  \href{https://mingukkang.github.io/GigaGAN/}{GIGAgan}

  \begin{itemize}
   
  \item
    \href{https://github.com/lucidrains/gigagan-pytorch}{implementation}
  \end{itemize}
\item
  \href{https://github.com/danielgatis/rembg}{GitHub -
  danielgatis/rembg: Rembg is a tool to remove images background
  (other)}
\item
  \href{https://github.com/kanewallmann/dreambooth-stable-diffusion}{GitHub
  - kanewallmann/Dreambooth-Stable-Diffusion: Implementation of
  Dreambooth (https://arxiv.org/abs/2208.12242) with Stable Diffusion
  (tweaks focused on training faces) (other)}
\item
  \href{https://github.com/sedthh/pyxelate}{GitHub - sedthh/pyxelate:
  Python class that generates pixel art from images (other)}
\item
  \href{https://github.com/upscayl/upscayl}{GitHub - upscayl/upscayl:  
  Upscayl - Free and Open Source AI Image Upscaler for Linux, MacOS and
  Windows built with Linux-First philosophy. (other)}
\item
  \href{https://github.com/YuxinWenRick/hard-prompts-made-easy}{GitHub -
  YuxinWenRick/hard-prompts-made-easy: Contribute to
  YuxinWenRick/hard-prompts-made-easy development by creating an account
  on GitHub.}
\item
  \href{https://civitai.com/models/16768/civitai-helper-sd-webui-civitai-extension}{Civitai
  Helper: SD Webui Civitai Extension bar{} Stable Diffusion Other
  bar{} Civitai: Now, we finally have a Civitai SD webui
  extension!! Update: 1.5.7 is here, if youquotesingle re using
  localization extension, like Asian lanuage UI, you need ...}
\item
  \href{https://github.com/YuxinWenRick/hard-prompts-made-easy}{GitHub -
  YuxinWenRick/hard-prompts-made-easy: Contribute to
  YuxinWenRick/hard-prompts-made-easy development by creating an account
  on GitHub.}
\item
  \href{https://twitter.com/abhi1thakur/status/1645669023726592007}{StableSam
  meta segmentation plus SD inpainting}
\item
  \href{https://github.com/houseofsecrets/SdPaint}{Realtime scribble}
\item
  Stable diffusion
\item
  \href{https://jalammar.github.io/illustrated-stable-diffusion/}{Illustrated
  overview}
\item
  \href{https://www.thosesixfaces.com/post/stable-diffusion-getting-started-windows}{Automatic1111
  GUI and user guide}
\item
  \href{https://github.com/Vetchems/sd-civitai-browser}{citivia browser}
\item
  \href{https://github.com/AUTOMATIC1111/stable-diffusion-webui}{Automatic
  WebUI}
\item
  \href{https://github.com/comfyanonymous/ComfyUI}{ComfyUI nodes based}
\item
  prompt engineering links
\item
  https://phraser.tech/
\item
  \href{https://docs.google.com/document/d/1SaQx1uJ9LBRS7c6OsZIaeanJGkUdsUBjk9X4dC59BaA/edit\#}{Artist
  keywords that are known to work}
\item
  Structure tips TL;DR
\item
  This is absolutely the most important one.\\
  Here I clearly describe the subject, without complex jargon or
  words.\\
  Keep this short, concise, and direct to your subject
\item
  Instead of creating a very long phrase, break this into 2.\\
  The first line is the key one, and in the second one you can reiterate
  making the subject stand even more
\item
  Every subject requires specific words, use your imagination and go
  wild.\\
  It wonquotesingle t hurt using interesting words, but avoid
  adding 1000 of them. It wonquotesingle t make the image any
  better (actually will mess up with your prompt
\item
  In the last section, I keep the aspect ratio, resolution, quality,
  stylized, and so on. You can add these in the beginning but I prefer
  to keep my structure very simple and clean\\
  You see, you donquotesingle t need much more. Literally 3/4
  sections.
\item
  \href{https://lexica.art/}{Lexica}
\item
  \href{https://docs.google.com/document/d/11WlzjBT0xRpQhP9tFMtxzd0q6ANIdHPUBkMV-YB043U/edit\#}{Dall-E
  prompt engineering}
\item
  \href{https://publicprompts.art/}{public prompts guy}
\item
  \href{https://christiancantrell.com/\#ai-ml}{Photoshop plugin}
\item
  Dreambooth retraining for faces
\item
  \href{https://pastebin.com/xcFpp9Mr}{windows instructions}
\item
  \href{https://discord.com/channels/1023277529424986162/}{Discord
  server}
\item
  \href{https://github.com/nitrosocke/dreambooth-training-guide/blob/main/README.md\#how-to-fine-tune-stable-diffusion-20}{dreambooth
  for SD2}
\item
  Birme image resizer
\item
  \href{https://www.youtube.com/watch?v=Bdl-jWR3Ukc\&t=34}{2 hour
  tutorial}
\item
  \href{https://www.youtube.com/watch?v=s25hcW4zq4M}{inject your face
  into any model (dreambooth)}
\item
  \href{https://github.com/nitrosocke/dreambooth-training-guide}{Guide
  for dreambooth}
\item
  \href{https://github.com/ShivamShrirao/diffusers/tree/main/examples/dreambooth}{Shivram}
\item
  \href{https://miro.com/app/board/uXjVPzJyAtU=/}{Progen photorealism
  Miro guide}
\item
  \href{https://github.com/2kpr/dreambooth-tokens}{rare dreambooth
  tokens}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/10gs4s2/new_expert_tutorial_for_textual_inversion_text/}{Textual
  inversion}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/xgurs3/testing_img2img_batch_processing_i_convert_this/}{Img2Img
  guide from reddit for face mapping}
\item
  \href{https://github.com/rinongal/textual_inversion}{textual inversion
  cheaper training}
\item
  \href{https://danieljeffries.substack.com/p/the-turning-point-for-truly-open?sd=pf}{CIO
  blog post}
\item
  \href{https://www.youtube.com/watch?v=lHcPtbZ0Mnc}{google stable
  diffusion}
\item
  \href{https://github.com/bloc97/CrossAttentionControl}{Cross attention
  replace named items}
\item
  \href{https://the-decoder.com/stable-diffusion-could-soon-generate-images-much-faster/}{256
  x faster speedup}
\item
  \href{https://github.com/VoltaML/voltaML-fast-stable-diffusion}{VoltaML
  acceleration}
\item
  \href{https://www.youtube.com/watch?v=AeDngG9kQNI}{Depth map into
  blender from SD2}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/z622mp/trained_midjourney_embedding_on_stable_diffusion/}{midjourney
  tweaks}

  \begin{itemize}
   
  \item
    \href{https://civitai.com/models/1253/anthro}{and another}
  \end{itemize}
\item
  \href{https://rentry.org/sdupdates3}{Updates Pastebin}
\item
  \href{https://www.heroo.ai/}{Game development using SD}
\item
  \href{https://github.com/mattjaybe/sd-wildcards}{Wildcard manager
  using ChatGPT}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/10c9kg8/depth2img_works_well_for_text_inputs/}{Depth2Img
  for text}
\item
  \href{https://dreamlike.art/guides/using-openai-chat-gpt-to-write-stable-diffusion-prompts}{train
  chat GPT to write prompts}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/10no6tp/non_destructive_image_variation_in_text2image/}{non
  destructive image manipulation using seeds}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/10l74sl/instruct_pix2pix_is_amazing_inpaintingimg2img/}{Instruct
  pix2pix}

  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/10tjzmf/instructpix2pix_is_built_straight_into_the/}{reddit
    post}
  \end{itemize}
\item
  \href{https://www.youtube.com/watch?v=XiKyEKJrTLQ}{Attention heatmap
  for prompts (youtube)}
\item
  \href{https://rentry.org/RentrySD/}{enormous link roundup}
\item
  \href{https://github.com/hoblin/prompt-master}{Prompt master
  variations management}
\item
  \href{https://huggingface.co/congazverse/worldBuilder}{panoramic world
  builder}
\item
  \href{https://github.com/abdullahalfaraj/auto-photoshop-stablediffusion-plugin}{GitHub
  - AbdullahAlfaraj/Auto-Photoshop-StableDiffusion-Plugin: A
  user-friendly plug-in that makes it easy to generate stable diffusion
  images inside Photoshop using Automatic1111-sd-webui as a backend.,A
  user-friendly plug-in that makes it easy to generate stable diffusion
  images inside Photoshop using Automatic1111-sd-webui as a backend. -
  GitHub - AbdullahAlfaraj/Auto-Photoshop-StableDiffusion-Plugin: A
  user-friendly plug-in that makes it easy to generate stable diffusion
  images inside Photoshop using Automatic1111-sd-webui as a backend.}
\item
  \href{https://github.com/ashawkey/stable-dreamfusion}{GitHub -
  ashawkey/stable-dreamfusion: A pytorch implementation of text-to-3D
  dreamfusion, powered by stable diffusion. , A pytorch implementation
  of text-to-3D dreamfusion, powered by stable diffusion. - GitHub -
  ashawkey/stable-dreamfusion: A pytorch implementation of text-to-3D
  dreamfusion, powered by stable diffusion.}
\item
  \href{https://github.com/nitrosocke/dreambooth-training-guide/blob/main/readme.md\#how-to-fine-tune-stable-diffusion-20}{Fine
  tune stable diffusion}
\item
  \href{https://github.com/sanster/lama-cleaner}{GitHub -
  Sanster/lama-cleaner: Image inpainting tool powered by SOTA AI Model.
  Remove any unwanted object, defect, people from your pictures or erase
  and replace(powered by stable diffusion) any thing on your pictures. ,
  Image inpainting tool powered by SOTA AI Model. Remove any unwanted
  object, defect, people from your pictures or erase and replace(powered
  by stable diffusion) any thing on your pictures. - GitHub -
  Sanster/lama-cleaner: Image inpainting tool powered by SOTA AI Model.
  Remove any unwanted object, defect, people from your pictures or erase
  and replace(powered by stable diffusion) any thing on your pictures.}
\item
  \href{https://holovolo.tv}{holovolo - immersive volumetric VR180
  videos and photos, and 3D stable diffusion, for Quest and WebVR ,-}
\item
  \href{https://jalammar.github.io/illustrated-stable-diffusion/}{The
  Illustrated Stable Diffusion Jay Alammar Visualizing machine learning
  one concept at a time.}
\item
  ControlNet
\item
  \href{https://huggingface.co/spaces/weizmannscience/multidiffusion-region-based}{Multidiffusion
  Spatial Controls - a Hugging Face Space by weizmannscience}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11fpcb1/testing_controlnet_on_unreal_engine_5/}{Testing
  ControlNet on Unreal Engine 5 : r/StableDiffusion}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11mzdxm/lineart_to_photoreal/}{LineArt
  to PhotoReal : r/StableDiffusion}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11mwzsz/convert_any_image_to_lineart_using_controlnet/}{Convert
  Any Image To Lineart Using ControlNet! : r/StableDiffusion}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11ah3nv/how_to_use_controlnet_to_make_incredible_fully/}{How
  to use Controlnet to make INCREDIBLE fully customizable Txt2Img
  templates : r/StableDiffusion}
\item
  \href{https://www.youtube.com/watch?v=vZ3W62dxuXI}{regional prompting
  tutorial}
\item
  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/1148x38/tencent_ai_just_release_their_method_and_code/}{Tencent
    AI just release their method and code very similar to ControlNet :
    r/StableDiffusion}
  \end{itemize}
\item
  GitHub - lllyasviel/ControlNet: Let us control diffusion models!
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11owo31/something_that_might_help_ppl_with_posing/}{Controlnet
  and character posing reddit post}
\item
  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/1148x38/tencent_ai_just_release_their_method_and_code/}{Tencent
    AI just release their method and code very similar to ControlNet :
    r/StableDiffusion}
  \end{itemize}
\item
  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/11rfol4/controlnet_character_design_workflow_links_in/}{ControlNet
    Character Design Workflow (links in comment) : r/StableDiffusion}
  \end{itemize}
\item
  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/StableDiffusion/comments/11rfol4/controlnet_character_design_workflow_links_in/}{ControlNet
    Character Design Workflow (links in comment) : r/StableDiffusion}
  \end{itemize}
\item
  \href{https://twitter.com/TomLikesRobots/status/1628100062910857217}{Twitter
  thread on consistency settings}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/125m56z/smooth_animation_with_controlnet_and_regional/}{Smooth
  animation with controlnet}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/127wub7/to_make_a_video_with_multiple_scenes_using_only/}{Multi
  scene videos using automatic1111}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12o8qm3/finally_installed_the_newer_controlnet_models_a/}{Controlnet
  1.1}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12z6rh5/half_real_converting_cowboy_bebop_spike_vs/}{Anime
  fight workflow}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/116ki29/comment/j97jac3/}{reddit
  educational links}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11pcsxe/just_discovered_a_useful_trick_for_getting_good/}{Negative
  prompt hack tip}
\item
  \href{https://github.com/justinpinkney/stable-diffusion/blob/main/notebooks/imagic.ipynb}{Modify
  images with text}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11u2p0u/lazy_guide_to_photorealistic_images/}{Photorealism}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/127gck9/sdtools_v16/}{sdtools
  image v 1.6}
\item
  \href{https://civitai.com/models/9409/anything-v5-or-anything-diffusion-original}{Anything
  v5 model on civitia}
\item
  nice models
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/100tp0v/protogenx34_has_absolutely_amazing_detail/}{Protogen3
  model is nice}
\item
  \href{https://civitai.com/models/5378/spirited-away-general-model-15}{spirited
  away model}
\item
  SPYGB for digital artists
\item
  project unity engine beta 2
\item
  realistic vision 1.2
\item
  \href{https://civitai.com/models/5271/style-info-an-embedding-for-infographic-style-art}{Infographic
  style}
\item
  video
\item
  Interpolation and interframe consistency
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/114zmh3/controlnet_and_ebsynth_make_incredible_temporally/}{controlnet
  and ebsynth temporal consistency}
\item
  \href{https://tsaishien-chen.github.io/MCDiff/}{Motion-Conditioned
  Diffusion Model for Controllable Video Synthesis}
\item
  \href{https://twitter.com/cut_pow/status/1576748659051749377}{Interframe
  consistency is now here}
\item
  \href{https://film-net.github.io/}{Interpolation between two frames}
\item
  \href{https://film-net.github.io/}{FILM frame interpolator}
\item
  \href{https://www.youtube.com/c/RunwayML}{Runway AI video editing}
\item
  \href{http://zeyuan-chen.com/VideoINR/}{Video slowmo and enhance}
\item
  \href{https://github.com/HelixNGC7293/DeforumStableDiffusionLocal}{deforum
  stable diffusion video}
\item
  \href{https://phenaki.video/}{Phenaki}
\item
  Collaborative video pipeline
\item
  \href{https://magicvideo.github.io/}{Magicvideo (faster)}
\item
  \href{https://studios.disneyresearch.com/2022/11/30/production-ready-face-re-aging-for-visual-effects/}{Production
  ready re aging}
\item
  \href{https://arxiv.org/abs/2202.00512}{distilled models for 25fps}
\item
  \href{https://www.linkedin.com/posts/rainisto_stablediffusion-musicvideo-remix-activity-7018207241522614272-YT1y?utm_source=share\&utm_medium=member_desktop}{Stable
  warpfusion}
\item
  \href{https://www.synthesia.io/}{Video talking heads from text
  service}
\item
  \href{https://tuneavideo.github.io/}{Tune a video}
\item
  \href{https://vidyo.ai/}{Vidyo: Generates videos for social networks
  from longer videos.}
\item
  \href{https://sites.google.com/view/stylegan-t}{Stylegan-T video
  transformer from google}
\item
  \href{https://github.com/proceduralit/StableDiffusion_Houdini}{Houdini}
\item
  \href{https://dreamix-video-editing.github.io/}{Dream Mix video to
  video remix}
\item
  \href{https://github.com/megvii-research/ECCV2022-RIFE}{RIFE frame
  interpolation}
\item
  \href{https://www.youtube.com/watch?v=4uzzD9sD-PI}{Synthesia corporate
  video generation}
\item
  \href{https://colab.research.google.com/github/dvschultz/ml-art-colabs/blob/master/Pix2PixHD_Next_Frame_Prediction.ipynb}{pix2pixHD
  nextframe google colab}
\item
  \href{https://github.com/TSFSean/InvokeAI-DiffusionCraftAI}{minecraft
  demo codebase}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/zecyc7/mixamo_animations_stable_diffusion_v2_depth2img/}{animation
  from mixamo}
\item
  \href{https://github.com/isl-org/PhotorealismEnhancement}{Intel
  enhance photorealism in realtime}
\item
  custom SD video to video script
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11okvc8/how_about_another_joke_murraaaay/}{consistency
  tools for character tooning}
\item
  \href{https://twitter.com/mreflow/status/1637957302073565184}{9 new
  tools}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11w0ba9/modelscope_17b_text2video_model_is_now_available/}{Automatic1111
  plugin}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/11f8i0g/next_frame_prediction_with_controlnet/}{Next
  frame prediction with controlnet}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/1244h2c/will_smith_eating_spaghetti/}{Will
  smith eating spaghetti}
\item
  \href{https://www.youtube.com/watch?v=sVmi2Yp43c0\&t=22}{Transform
  Video to Animation in Stable Diffusion bar{} How to Install +
  BEST Consistency Settings: Learn how to use AI to create animations
  from real videos. Wequotesingle ll use Stable Diffusion and other
  tools for maximum consistency Project Files:https://bit.ly/3...}
\item
  \href{https://www.kombitz.com/2023/03/28/how-to-use-modelscope-text2video-with-automatic1111s-stable-diffusion-web-ui/}{How
  to Use ModelScope text2video with Automatic1111's Stable Diffusion Web
  UI bar{} kombitz: Enable the Extension Click on the Extension tab
  and then click on Install from URL. Enter
  https://github.com/deforum-art/sd-webui-modelscope-text2video in the
  URL box and click on Install. Click on Installed and click on Apply
  and restart UI. Go to your stable-diffusion-webui/models folder and
  create a folder called ModelScope and then create a folder called t2v
  under ModelScope. This is your models folder for text2video.}
\item
  \href{https://github.com/Picsart-AI-Research/Text2Video-Zero}{GitHub -
  Picsart-AI-Research/Text2Video-Zero: Text-to-Image Diffusion Models
  are Zero-Shot Video Generators: Text-to-Image Diffusion Models are
  Zero-Shot Video Generators - GitHub -
  Picsart-AI-Research/Text2Video-Zero: Text-to-Image Diffusion Models
  are Zero-Shot Video Generators}
\item
  \href{https://yingqinghe.github.io/LVDM/}{LVDM for long video
  creation}
\item
  \href{https://lukashoel.github.io/text-to-room/}{The Text2Room
  algorithm generates textured 3D meshes from a given text prompt by
  leveraging pre-trained 2D text-to-image models. The core idea is to
  select camera poses that will result in a seamless, textured 3D mesh.
  The algorithm iteratively fuses scene frames with the existing
  geometry to create the final mesh. Evaluation shows that the algorithm
  is able to generate room-scale 3D geometry with compelling textures
  from only text as input.}
\item
  \href{https://bennyguo.github.io/vmesh/}{The VMesh system models a
  scene with a triangular mesh and a sparse volume for efficient view
  synthesis. It is trained on multi-view images of an object to create a
  contiguous representation of the objectquotesingle s surface and
  volume. This representation is then used to generate a simplified
  triangular mesh and a sparse volume, which can be stored and rendered
  efficiently. The system is designed for real-time applications and can
  render at 2K 60FPS on common consumer devices.}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12sd4bi/results_from_latest_version_of_temporal_stable/}{Temporal
  stable automatic plugin}
\item
  \href{https://buff.ly/41FgQrb}{We present a method for high-resolution
  video synthesis using latent diffusion models (LDMs). Our approach
  first pre-trains an LDM on images, then introduces a temporal
  dimension to the latent space diffusion model and fine-tunes it on
  encoded image sequences (i.e. videos). We focus on two real-world
  applications: simulation of in-the-wild driving data and creative
  content creation with text-to-video modeling. Our method achieves
  state-of-the-art performance on real driving videos of 512 x 1024
  resolution. Additionally, our approach can leverage off-the-shelf
  pre-trained image LDMs, turning the publicly available,
  state-of-the-art text-to-image LDM Stable Diffusion into an efficient
  and expressive text-to-video model.}
\item
  \href{https://github.com/volotat/SD-CN-Animation}{This script allows
  for the automation of video stylization using StableDiffusion and
  ControlNet.}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12otdo0/the_secret_to_really_easy_videos_in_a1111_easier/}{Really
  easy videos in A1111}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/12nwpdx/dancer_4_keyframes_guide_and_source_files_for/}{Dancer
  4 keyframes, low noise, controlnet approach}
\item
  Unreal convergence
\item
  \href{https://www.linkedin.com/posts/eric-vyacheslav-156273169_an-amazing-landscape-animation-created-in-activity-7021136593314791424-fq_C/?originalSubdomain=lt}{Midjourney
  and Unreal landscape}
\item
  \href{https://www.reddit.com/r/StableDiffusion/comments/10rr99t/mocap_unreal_engine_warpfusion/}{MoCap
  Unreal and Warpfusion}
\item
  Coding support
\item
  \href{https://buttondown.email/hillelwayne/archive/programming-ais-worry-me/}{Programming
  AIs worry me   Buttondown:}
\item
  \href{https://about.sourcegraph.com/blog/cheating-is-all-you-need}{Stop
  whining blog post}
\item
  \href{https://evanthebouncy.github.io/program-synthesis-minimal/generation-with-llm/}{blog
  post on LLMs for code}
\item
  \href{https://github.com/emcf/engshell/tree/main}{Engshell shell LLM
  extension}
\item
  \href{https://useadrenaline.com/app}{Github assist}
\item
  \href{https://huggingface.co/ehartford/alpaca1337-13b-4bit/tree/main}{Locally
  run 13B coding optimised model}
\item
  \href{https://buttondown.email/hillelwayne/archive/programming-ais-worry-me/}{Programming
  AIs worry me   Buttondown (other)}
\item
  Hardware
\item
  \href{https://www.marktechpost.com/2022/10/27/ibm-research-introduces-artificial-intelligence-unit-aiu-its-first-complete-system-on-chip-designed-to-run-and-train-deep-learning-models-faster-and-more-efficiently-than-a-general-purpose-cpu/}{IBM
  custom board}
\item
  \href{https://www.okdo.com/p/nvidia-jetson-agx-orin-64gb-developer-kit/}{Nvidia
  jetson AI}
\item
  \href{https://www.theverge.com/2023/2/23/23611668/ai-image-stable-diffusion-mobile-android-qualcomm-fastest}{Qualcomm
  phone SD}
\item
  \href{https://www.esperanto.ai/}{Esperanto RISC V}
\item
  \href{https://hdh4797.wixsite.com/dhan/project-1}{}
\item
  \href{https://developers.google.com/learn/topics/on-device-ml}{Google
  android etc}
\item
  HCI

  \begin{itemize}
   
  \item
    \href{https://www.from-the-interface.com/wrist-interfaces/}{Metaquotesingle s
    wrist reader}
  \item
    \href{https://github.com/Shopify/handy}{Shopify handy}
  \end{itemize}
\item
  \href{https://timdettmers.com/2023/01/16/which-gpu-for-deep-learning/}{Comparison
  of GPUs}
\item
  LLM and creating new LLM

  \begin{itemize}
   
  \item
    Multiligual and abstract translation
  \end{itemize}
\item
  Infosec, privacy, ethics

  \begin{itemize}
   
  \item
    \href{https://ico.org.uk/for-organisations/guide-to-data-protection/key-dp-themes/guidance-on-ai-and-data-protection/how-should-we-assess-security-and-data-minimisation-in-ai/}{AI
    security considerations}
  \end{itemize}
\item
  \href{https://arstechnica.com/information-technology/2023/02/sci-fi-becomes-real-as-renowned-magazine-closes-submissions-due-to-ai-writers/}{Sci-fi
  becomes real as renowned magazine closes submissions due to AI
  writers: Clarkesworld wrestles with flood of machine-made
  submissions---over 500 in Feb. alone.}
\item
  \href{https://www.lesswrong.com/tag/ai}{Lesswrong AI section}
\item
  \href{https://www.forbes.com/sites/jackkelly/2023/03/31/goldman-sachs-predicts-300-million-jobs-will-be-lost-or-degraded-by-artificial-intelligence/?sh=3af7314e782b}{Goldman
  Sachs Predicts 300 Million Jobs Will Be Lost Or Degraded By Artificial
  Intelligence: Goldman Sachs maintains that if generative AI lives up
  to its hype, the workforce in the United States and Europe will be
  upended. The bank estimates 300 million jobs could be lost or
  diminished due to this fast-growing technology.}
\item
  \href{https://blog.medium.com/how-were-approaching-ai-generated-writing-on-medium-16ee8cb3bc89}{Medium
  listing approachs}
\item
  \href{https://www.theguardian.com/technology/2023/mar/23/tech-guru-jaron-lanier-the-danger-isnt-that-ai-destroys-us-its-that-it-drives-us-insane}{Drives
  us mad, Guardian}
\item
  \href{https://www.artisana.ai/articles/eus-ai-act-stricter-rules-for-chatbots-on-the-horizon}{Chatbots
  must disclose sources or face ban}
\item
  Specialist model use cases
\item
  Medical
\item
  Financial / tax
\item
  Compliance
\item
  Companionship
\item
  Travel
\item
  Law
\item
  Programming
\item
  Copywriting
\item
  Editorial
\item
  Segment and identify
\item
  \href{https://segment-anything.com/}{Segment anything from Meta}
\item
  \href{https://deci.ai/blog/yolo-nas-foundation-model-object-detection/}{YOLO
  detect anything}
\item
  Lora
\item
  \href{https://discord.com/channels/1086739839761776660/1087508281758584852}{alpaca
  lora training}

  \begin{itemize}
   
  \item
    \href{https://github.com/tloen/alpaca-lora}{Github}
  \end{itemize}
\item
  \href{https://github.com/oobabooga/text-generation-webui/commit/09d8119e3cf36257496acfb44e6445a9f40c3d02}{CPU
  offload lora training}
\item
  \href{https://rentry.org/llama-tard-v2\#llama-int8-4bit-chatbot-guide-v2}{llamatard
  4bit chat instructions}
\item
  \href{https://civitai.com/models/22530}{The text provides a guide on
  how to make your own Loras, which are easy and free to create. The
  process is described in detail, and the text includes instructions on
  how to create and customize your own Loras.}
\item
  Deep retraining
\item
  Deepspeed chat retraining in hours
\item
  \href{https://github.com/lvwerra/trl}{TRL - Transformer Reinforcement
  Learning}
\item
  Hardware requirements for retraining (links to state of the art)
\item
  \href{https://www.databricks.com/blog/2023/03/20/fine-tuning-large-language-models-hugging-face-and-deepspeed.html}{Finetuning
  blog post}
\item
  Pruning
\item
  \href{https://arxiv.org/abs/1803.03635}{Seems that both 4 bit and
  straight up pruning donquotesingle t harm the models much}
\item
  Merging
\item
  \href{https://github.com/TehVenomm/LM_Transformers_BlockMerge}{diffusion
  style LLM block merging}
\item
  \href{https://docs.google.com/document/d/1JCzJ1wdBMBVwsFW4CWGUbX-YEDXB0yS4mfFbvwPLQrI/edit}{Domain
  expert model merging}
\item
  Toolkits and distributed
\item
  \href{https://github.com/tensorflow/mesh}{                (mtf) is a
  language for distributed deep learning, capable of specifying a broad
  class of distributed tensor computations. The purpose of Mesh
  TensorFlow is to formalize and implement distribution strategies for
  your computation graph over your hardware/processors. For example:
  "Split the batch over rows of processors and split the units in the
  hidden layer across columns of processors." Mesh TensorFlow is
  implemented as a layer over TensorFlow.}
\item
  \href{https://github.com/OpenBMB/BMTrain}{        is an efficient
  large model training toolkit that can be used to train large models
  with tens of billions of parameters. It can train models in a
  distributed manner while keeping the code as simple as stand-alone
  training.}
\item
  \href{https://colossalai.org/}{        -   provides a collection of
  parallel components for you. It aim to support us to write our
  distributed deep learning models just like how we write our model on
  our laptop. It provide user-friendly tools to kickstart distributed
  training and inference in a few lines.  Open source solution
  replicates ChatGPT training process.Ready to go with only 1.6GB GPU
  memory and gives you 7.73 times faster training:
  https://lnkd.in/gp4XTCnz}
\item
  \href{https://github.com/young-geng/EasyLM}{EasyLM one stop scaleable
  toolkit}
\item
  \href{https://github.com/gmpetrov/databerry}{databerry training and
  deployment}
\item
  \href{https://arxiv.org/abs/2209.01188}{Petals collaborative fine
  tuning}
\item
  \href{https://opensource.googleblog.com/2023/03/openxla-is-ready-to-accelerate-and-simplify-ml-development.html}{Goodle
  openXLA training accelerator}
\item
  \href{https://twitter.com/BrianRoemmele/status/1637871062246649856}{Use
  GPT API as a GAN (twitter thread)}
\item
  \href{https://github.com/bigscience-workshop/petals}{Bigscience petals
  run training through torrents}
\item
  \href{https://www.reddit.com/r/MachineLearning/comments/136vt7b/p_airoboros_a_rewrite_of_selfinstructalpaca/}{airoboros\_a\_rewrite\_of\_selfinstructalpaca/}
\item
  \href{https://arxiv.org/abs/2304.12210}{A Cookbook of Self-Supervised
  Learning}
\item
  \href{https://github.com/nebuly-ai/nebullvm/tree/main/apps/accelerate/chatllama}{ChatLLaMA
  is a library that allows you to create hyper-personalized ChatGPT-like
  assistants using your own data and the least amount of compute
  possible. Instead of depending on one large assistant that ``rules us
  all'', we envision a future where each of us can create our own
  personalized version of ChatGPT-like assistants.}
\item
  \href{https://abuqader.substack.com/p/releasing-alpaca-30b}{Substack
  on retraining a 30B model in an A100}
\item
  \href{https://github.com/alpa-projects/alpa}{}

       is a system for training and serving large-scale neural networks.
  Scaling neural networks to hundreds of billions of parameters has
  enabled dramatic breakthroughs such as GPT-3, but training and serving
  these large-scale neural networks require complicated distributed
  system techniques. Alpa aims to automate large-scale distributed
  training and serving with just a few lines of code.

   Alpa:

   Serving OPT-175B, BLOOM-176B and CodeGen-16B using Alpa:
  https://lnkd.in/g\_ANHH6f
\item
  \href{https://github.com/NVIDIA/Megatron-LM}{        -   / Megatron is
  a large, powerful transformer developed by the Applied Deep Learning
  Research team at NVIDIA. Below repository is for ongoing research on
  training large transformer language models at scale. Developing
  efficient, model-parallel (tensor, sequence, and pipeline), and
  multi-node pre-training of transformer based models such as GPT, BERT,
  and T5 using mixed precision.  pretrain\_gpt3\_175B.sh:
  https://lnkd.in/gFA9h8ns}
\item
  \href{https://bair.berkeley.edu/blog/2023/04/03/koala/?ref=emergentmind}{Koala
  paper on training with minimal noise for chatbots}
\item
  \href{https://rubbrband.com/}{rubbrband github auto deployments}
\item
  \href{https://github.com/Mooler0410/LLMsPracticalGuide}{Practical
  guide github and paper with branching diagram}
\item
  Alpaca
\item
  \href{https://crfm.stanford.edu/2023/03/13/alpaca.html}{Launch post
  with links}
\item
  \href{https://github.com/oobabooga/text-generation-webui/discussions/727}{Anonymous
  alpaca gpt train}
\item
  Llama
\item
  \href{https://aituts.com/llama/}{Guide that worked for gradio}
\item
  \href{https://github.com/shawwn/llama-dl}{llama download from git}

  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/MachineLearning/comments/11kwdu9/d_tutorial_run_llama_on_8gb_vram_on_windows/}{running
    in venv}
  \item
    \href{https://rentry.org/llama-tard-v2}{int8 guide}
  \item
    https://www.reddit.com/r/LocalLLaMA/comments/1227uj5/my\_experience\_with\_alpacacpp/
  \item
    \href{https://github.com/cocktailpeanut/dalai}{CocktailPeanut
    Implementation}
  \end{itemize}
\item
  \href{https://github.com/oobabooga/text-generation-webui}{Oogabooga
  LLM github gradio}
\item
  \href{https://github.com/oobabooga/text-generation-webui/issues/40\#issuecomment-1412038622}{deepspeed
  notes}
\item
  \href{https://github.com/oobabooga/text-generation-webui/tree/main/extensions/whisper_stt}{whisper
  voice to prompt}
\item
  \href{https://github.com/oobabooga/text-generation-webui/blob/main/extensions/silero_tts/script.py}{text
  to speech}
\item
  erebus
\item
  How to install

  \begin{itemize}
   
  \item
    patch
  \item
    ensure python 3.10.9, use proper venv
  \item
    cudnn as well as the drivers and normal reqs
  \item
    install plus all the requirements from the extensions
  \item
    make a startup script
  \end{itemize}
\item
  Dalai llama

  \begin{itemize}
   
  \item
    git clone the dalai from you desired github (i like the one from
    @cocktailpeanut and the @\#1 Dalai support (.pi)) go to the dalai
    folder and use npm install return your models for the dalai path
    models after that npx dalai@latest alpaca install
    your\_model\_version after that npx dalai@latest serve
  \end{itemize}
\item
  \href{https://rentry.org/llama-tard-v2}{llama tard v2}
\item
  \href{https://github.com/ortegaalfredo/celery-ai/blob/main/discord/bot.py}{Discord
  llama based chatbot}
\item
  \href{https://github.com/lm-sys/FastChat}{FastChat based on llama 13b}
\item
  \href{https://github.com/oobabooga/text-generation-webui/wiki/LLaMA-model}{4bit
  30B linux integration}

  \begin{itemize}
   
  \item
    \href{https://github.com/facebookresearch/llama/issues/162}{persistence}
  \end{itemize}
\item
  \href{https://huggingface.co/Neko-Institute-of-Science/LLaMA-30B-4bit-128g/tree/main}{llama-30b-4bit-huggingface}
\item
  \href{https://github.com/ggerganov/llama.cpp/issues/22}{Llama CPP
  windows open ticket}

  \begin{itemize}
   
  \item
    \href{https://arstechnica.com/information-technology/2023/03/you-can-now-run-a-gpt-3-level-ai-model-on-your-laptop-phone-and-raspberry-pi/}{article
    on the implications}
  \end{itemize}
\item
  \href{https://github.com/BlinkDL/RWKV-LM}{Raven LLM RNN hybrid}

  \begin{itemize}
   
  \item
    \href{https://huggingface.co/BlinkDL/rwkv-4-raven}{raven model on
    huggingface}
  \item
    \href{https://github.com/harrisonvanderbyl/rwkv-cpp-cuda}{cpp
    implementation}
  \end{itemize}
\item
  \href{https://www.databricks.com/blog/2023/04/12/dolly-first-open-commercially-viable-instruction-tuned-llm}{Dolly
  open source}

  \begin{itemize}
   
  \item
    \href{https://github.com/databrickslabs/dolly/tree/master/data}{databricks
    repo}
  \end{itemize}
\item
  \href{https://github.com/hpcaitech/ColossalAI}{collosal AI Open source
  GPT attempt}
\item
  \href{https://huggingface.co/togethercomputer/GPT-NeoXT-Chat-Base-20B}{GPT-NeoXT-Chat-Base-20B
  human optimised free model}
\item
  \href{https://huggingface.co/notstoic/OPT-13B-Nerybus-Mix-4bit-128g}{Nerybus
  blend}
\item
  \href{https://github.com/openlm-research/open_llama}{OpenLlama}
\item
  \href{https://huggingface.co/lmsys/fastchat-t5-3b-v1.0}{Fastchat}
\item
  Vircuna

  \begin{itemize}
   
  \item
    \href{https://github.com/lm-sys/FastChat\#fine-tuning-vicuna-7b-with-local-gpus}{Vircuna
    7B}
  \item
    \href{https://www.reddit.com/r/LocalLLaMA/comments/1376oho/introducing_wizardvicunalm_combining_wizardlm_and/}{WizardVircua
    retrain}
  \item
    \href{https://huggingface.co/reeducator/vicuna-13b-free}{VircunaFree}
  \end{itemize}
\item
  \href{https://www.philschmid.de/sagemaker-fsdp-gpt}{How to scale LLM
  workloads to 20B+ with Amazon SageMaker using Hugging Face and PyTorch
  FSDP}
\item
  \href{https://www.together.xyz/blog/redpajama-models-v1}{Red Pajama}
\item
  \href{https://www.mosaicml.com/blog/mpt-7b}{Mozilla LLM (apache)}
\item
  \href{https://huggingface.co/openlm-research}{OpenLlama weights}
\item
  \href{https://github.com/abertsch72/unlimiformer}{Unlimited input}
\item
  \href{https://github.com/stability-AI/stableLM/}{This repository
  contains Stability AIquotesingle s development of the StableLM
  series of language models. The models are designed to be more stable
  and robust than traditional language models, and the repository
  includes code and examples for training and using the models.}
\item
  \href{https://github.com/microsoft/DeepSpeed}{          is an
  easy-to-use deep learning optimization software suite that enables
  unprecedented scale and speed for DL Training and Inference. Visit us
  at deepspeed.ai or our Github repo.  Megatron-LM GPT2 tutorial:
  https://lnkd.in/gXvPhXqb}
\item
  \href{https://blog.replit.com/llm-training}{The text provides
  instructions on how to train your own large language models using
  Replit. It explains that you will need to first create a Replit
  account and then follow the instructions on the website.}
\item
  \href{http://Futurepedia.io}{Futurepedia is the largest AI tools
  directory, with over 700 tools in various categories. It is updated
  daily, and features search and filter options to help you find the
  right tool for your needs.}
\item
  \href{https://github.com/gitnomad24601/ShogScript}{GitHub -
  gitnomad24601/ShogScript: ShogScript: The GitHub repository
  "ShogScript" contains a proof-of-concept pseudocode for GPT-4 AI
  interactions, ideal for storytelling \& communication. The code is
  released under the MIT license.}
\item
  \href{https://magazine.sebastianraschka.com/p/understanding-large-language-models}{Understanding
  Large Language Models: A Cross-Section of the Most Relevant Literature
  To Get Up to Speed}
\item
  \href{https://github.com/oobabooga/text-generation-webui/pull/1229}{The
  text describes a change to support the GPTQ triton commit c90adef.
  This change allows for the disabling of quant attention.}
\item
  \href{https://arxiv.org/abs/2305.02301}{2000x performance improvement
  paper}
\item
  \href{https://github.com/FMInference/FlexGen\#get-started-with-a-single-gpu}{Flexgen}
\item
  \href{https://github.com/johnsmith0031/alpaca_lora_4bit}{4bit
  compression}
\item
  \href{https://www.reddit.com/r/MachineLearning/comments/123b66w/dgpt4_might_be_able_to_tell_you_if_it_hallucinated/}{GPT4
  self hallucination checking}
\item
  \href{https://arxiv.org/abs/2301.00774}{Sparse LLM, half the size, all
  the power}
\item
  \href{https://github.com/togethercomputer/OpenChatKit}{Openchatkit
  tools for building chatbots}
\item
  \href{https://medium.com/@imicknl/how-to-create-a-private-chatgpt-with-your-own-data-15754e6378a1}{How
  to create a private ChatGPT with your own data: Learn the architecture
  and data requirements needed to create your own Q\&A engine with
  ChatGPT/LLMs.}
\item
  \href{https://github.com/neuml/txtchat}{txtchat in python}
\item
  \href{https://www.theverge.com/2023/3/7/23628673/chatgpt-slack-salesforce-einstein-ai-business-messaging}{Slack's
  new ChatGPT bot will talk to your colleagues for you - The Verge
  (other)}
\item
  \href{https://github.com/nomic-ai/gpt4all}{Gpt4all: a chatbot trained
  on a massive collection of clean assistant data including code,
  stories and dialogue}
\item
  \href{https://github.com/JushBJJ/Mr.-Ranedeer-AI-Tutor}{GPT4 tutor
  script}
\item
  \href{https://colab.research.google.com/github/TavernAI/TavernAI/blob/main/colab/GPU.ipynb}{TavernAI
  colab}
\item
  Local ChatGPT UI githubs

  \begin{itemize}
   
  \item
    https://github.com/patrikzudel/PatrikZeros-ChatGPT-API-UI
  \item
    https://github.com/mckaywrigley/chatbot-ui
  \item
    https://github.com/WongSaang/chatgpt-ui
  \item
    https://github.com/ztjhz/BetterChatGPT
  \item
    https://github.com/sahil280114/chatGPT-multimodal-bot
  \item
    \href{https://llm.report/}{Local report on usage costs}
  \end{itemize}
\item
  \href{https://github.com/jerryjliu/llama_index}{Llamaindex data
  connections}
\item
  \href{https://arxiv.org/pdf/2303.17580.pdf}{Jarvis / huggingface
  connect ML tools to LLMs}
\item
  Connect to the internet
\item
  \href{https://www.aomni.com/}{aomni: Aomni is an information retrieval
  AI agent that is able to find, extract, and process any data for you
  on the internet.}
\item
  \href{https://github.com/michaelthwan/searchGPT}{search based open
  source LLM MVP}
\item
  AutoGPT and similar
\item
  \href{https://github.com/Torantulino/Auto-GPT}{GitHub -
  Torantulino/Auto-GPT: An experimental open-source attempt to make
  GPT-4 fully autonomous.: An experimental open-source attempt to make
  GPT-4 fully autonomous. - GitHub - Torantulino/Auto-GPT: An
  experimental open-source attempt to make GPT-4 fully autonomous.}
\item
  \href{https://mobile.twitter.com/SullyOmarr/status/1645482778677452805}{AutoGPT
  twitter thread}
\item
  \href{https://godmode.space/}{Godmode.space automatic 3.5 task
  website}
\item
  Memory and data mining
\item
  \href{https://arxiv.org/abs/2304.03442}{Simulrum of human behaviour}
\item
  Vector databases
\item
  Pinecone
\item
  \href{https://sigmoidprime.com/post/searchthearxiv/}{Building a
  Semantic Search Engine With OpenAI and Pinecone:}
\item
  \href{https://leanpub.com/langchain/read}{Free langchain book}
\item
  \href{https://www.activeloop.ai/resources/ultimate-guide-to-lang-chain-deep-lake-build-chat-gpt-to-answer-questions-on-your-financial-data/}{ultimate
  guide to langchain}
\item
  \href{https://github.com/Oneirocom/Academy/blob/main/week3/_overview.md}{Memory
  seminar}
\item
  \href{https://arxiv.org/abs/2304.11062}{Experiments in 1 and 2 million
  token inputs}

  \begin{itemize}
   
  \item
    \href{https://github.com/booydar/t5-experiments}{github}
  \end{itemize}
\item
  \href{https://github.com/ausboss/Local-LLM-Langchain}{Local LLM
  langchain memory in Jupyter}

  \begin{itemize}
   
  \item
    \href{https://huggingface.co/LangChainDatasets}{langchain datasets}
  \end{itemize}
\item
  \href{https://github.com/HazyResearch/evaporate}{Evapourate data lakes
  into LLMs}
\item
  \href{https://github.com/pashpashpash/vault-ai}{Vault AI chunker}
\item
  \href{https://powerusers.microsoft.com/t5/Calling-Actions-from-PVA/Use-GPT-ChatGPT-to-summarize-and-reference-the-results-from-an/td-p/2101639}{Summarise
  internal company links}
\item
  \href{https://www.reddit.com/r/MachineLearning/comments/12oh07a/p_chat_with_any_github_repo_code_understanding/}{Chat
  with any github repository}
\item
  \href{https://useadrenaline.com/app}{Understand a codebase in github
  with GPT}
\item
  \href{https://www.reddit.com/r/MachineLearning/comments/125qztx/d_the_best_way_to_train_an_llm_on_company_data/}{Best
  way to train an LLM on company data}
\item
  \href{https://medium.com/singapore-gds/integrating-chatgpt-with-internal-knowledge-base-and-question-answer-platform-36a3283d6334}{The
  text describes the process of integrating ChatGPT, a chatbot, with an
  internal knowledge base and question-answer platform. The goal is to
  improve the chatbotquotesingle s ability to provide accurate and
  relevant information. The process involves training the chatbot on a
  variety of data sources, including the internal knowledge base.}
\item
  Character injection

  \begin{itemize}
   
  \item
    \href{https://oobabooga.github.io/character-creator.html}{json
    builder}
  \item
    \href{https://huggingface.co/blog/trl-peft}{Huggingface commodity
    card retrainer}
  \end{itemize}
\item
  \href{https://simonwillison.net/2023/Apr/14/worst-that-can-happen/}{Prompt
  injection: what s the worst that can happen?}
\item
  \href{https://www.digitaltrends.com/computing/how-to-jailbreak-chatgpt/}{To
  jailbreak ChatGPT, you need to get it to really do what you want. This
  can be done by editing the source code or by using a third-party
  tool.}
\item
  General purpose super short prompt

  \begin{itemize}
   
  \item
    develop+extend+support(ideas), vocab(wide+natural+sophisticated),
    grammar(wide+flexible), cohesion(logical+smooth),
    clarity(precise+concise), engagement(attention+interest),
    mood(objective+explanatory), viewpoint(forward\_looking)
  \end{itemize}
\item
  \href{https://openreview.net/forum?id=92gvk82DE-}{Large Language
  Models are Human-Level Prompt Engineers: We propose an algorithm for
  automatic instruction generation and selection for large language
  models with human level performance.}
\item
  \href{https://georgesung.github.io/ai/llm-qa-eval-wikipedia/}{github
  of comparisons}
\item
  \href{https://georgesung.github.io/ai/llm-qa-eval-wikipedia/}{compare
  open source vs closed}
\item
  \href{https://github.com/FreedomIntelligence/LLMZoo}{LLM zoo}
\item
  \href{https://arxiv.org/abs/2303.11156}{Can AI-Generated Text be
  Reliably Detected?:}
\item
  \href{http://gptzero.me/}{gptzero spots AI authoring}
\item
  \href{https://gonzoknows.com/posts/GPTZero-Case-Study/}{GPTZero Case
  Study (Exploring False Positives): Introduction In this case study, I
  will be sharing the vast amounts of false positives current AI
  detection software gives, specifically for this case study I will be
  demonstrating GPTZero. I personally want to thank the supposed
  ``Healthcare professional'' who brought this to my attention via my
  contact link. It has motivated me to look more into this issue rather
  than just posting bypasses to these popular AI detection software
  programs, it will be only more beneficial to highlight their real
  usability in general.}
\item
  \href{https://nexus.snikpic.io}{NexusGPT is a freelancer platform that
  uses AI to help businesses find the right freelancers for their needs.
  The platform offers a variety of features to help businesses find the
  perfect freelancer for their project, including a searchable database
  of freelancers, a rating system, and a feature that allows businesses
  to post their project and receive bids from freelancers.}
\item
  \href{https://interestingengineering.com/innovation/radiogpt-worlds-first-ai-radio-station}{RadioGPT:
  quotesingle World's firstquotesingle{} AI-driven radio
  station is here (other)}
\item
  \href{https://github.com/MatveyM11/Mine-ChatGPT}{GitHub -
  MatveyM11/Mine-ChatGPT: OpenSourced ChatGPT downloader in markdown
  format. Download all text or markdown-styled code blocks Fear no more
  that servers are down, under high load or OpenAI adding a new feature.
  Keep all yours chatquotesingle s with you locally in the simple
  .md files.: OpenSourced ChatGPT downloader in markdown format.
  Download all text or markdown-styled code blocks Fear no more that
  servers are down, under high load or OpenAI adding a new feature. Keep
  all your...}
\item
  \href{https://github.com/allenai/mmc4}{MultimodalC4 is a multimodal
  extension of c4 that interleaves millions of images with text. The
  corpus contains over a billion images, and the text is interleaved
  with the images to provide context.}
\item
  \href{https://txt.cohere.ai/what-are-transformer-models/}{Transformers
  are a new type of machine learning model that have been making
  headlines recently. They are very good at keeping track of context,
  which is why the text they generate makes sense. In this blog post, we
  will go over their architecture and how they work.}
\item
  implementations

  \begin{itemize}
   
  \item
    pytorch/numpty
  \item
    tensorflow/jax
  \end{itemize}
\item
  \href{https://simonwillison.net/2023/Apr/2/calculator-for-words/}{Think
  of language models like ChatGPT as a ``calculator for words'': One of
  the most pervasive mistakes I see people using with large language
  model tools like ChatGPT is trying to use them as a search engine. As
  with other LLM \ldots{}}
\item
  \href{https://ihavemanythoughts.substack.com/p/peak-llm}{Peak LLM:
  Prompt injection might be just the beginning}
\item
  \href{https://sentic.net/language-models-as-inductive-reasoners.pdf}{Language
  models as inductive reasoners paper}
\item
  \href{https://github.com/jeffhj/LM-reasoning}{This repository contains
  a collection of papers and resources on Reasoning in Large Language
  Models. The papers survey the state of the art in this area, and
  discuss how large language models can be used to obtain emergent
  abilities.}
\item
  \href{https://mobile.twitter.com/omarsar0/status/1641788196550856704}{Full
  trainingset used by bloombergAI}
\item
  \href{https://www.linkedin.com/posts/zainkahn_1000-ai-tools-were-released-in-march-activity-7048285306101358592-4wAA?utm_source=share\&utm_medium=member_android}{Zain
  Kahn on LinkedIn reports that over 1,000 AI tools were released in
  March. He states that ChatGPT is just the tip of the iceberg, and that
  there are 20 AI tools that will transform productivity forever.}
\item
  \href{https://www.reddit.com/r/MachineLearning/comments/129wzdk/p_engshell_a_gpt4_driven_englishlanguage_shell/}{Language
  driven shell for OS (ooft)}
\item
  \href{https://www.linkedin.com/posts/ezra-eeman-8a5ba64_dpa-just-released-its-guidelines-for-the-activity-7048985893910519808-921y?utm_source=share\&utm_medium=member_android}{The
  text contains information on the release of guidelines by the DPA for
  the use of AI, as well as on similar efforts by other organizations.
  It also provides links to resources on the topic.}
\item
  \href{https://mind.ai/technology}{Mind AI team website}
\item
  \href{https://magazine.sebastianraschka.com/archive}{Ahead of AI
  substack}
\item
  \href{https://drive.google.com/file/d/1i4NJKAggS82wqMamCJ1OHRGgViuyoY6R/view}{Meta
  research paper}
\item
  \href{https://www.stateof.ai/}{State of AI report}
\item
  \href{https://www.medpagetoday.com/special-reports/exclusives/102705}{AI
  ML passes American medical exams}
\item
  \href{https://github.com/diego-vicente/som-tsp}{Travelling salesman
  problem}
\item
  \href{https://medium.com/@socialemail/how-diffusion-models-can-achieve-seemingly-arbitrarily-large-compression-ratios-through-learning-2b21a317a46a}{How
  the compression is so huge in diffusion models}
\item
  \href{https://udlbook.github.io/udlbook/}{Understanding deep learning
  book}
\item
  \href{https://github.com/SkalskiP/courses}{This repository is a
  collection of links to various courses and resources about Artificial
  Intelligence (AI).}
\item
  Distributed tech
\item
  \href{https://horde.koboldai.net/}{horde image and llm}
\item
  Browser based whole models
\item
  \href{https://developer.nvidia.com/blog/dask-tutorial-beginners-guide-to-distributed-computing-with-gpus-in-python/}{Nvidia
  DASK}
\item
  immersive spaces
\item
  Why you should use now generative AI in your metaverse company. Or
  maybe not - The Ghost Howls
  https://skarredghost.com/2023/02/11/generative-ai-metaverse-company/
\item
  \href{https://www.traffickinggame.com/ai-assisted-graphics/}{games
  dev}
\item
  \href{https://twitter.com/ronithhh/status/1641318606549176321}{Instant
  app from prompts}
\item
  \href{https://replit.com/@asrsubs/SkyRoads-GPT-4}{endless runner
  without any coding experience}
\item
  RP-Lidar + Raspberry pi + ROS RTAB-MAP

  \begin{itemize}
   
  \item
    \href{http://introlab.github.io/rtabmap/}{RTAB-Map}
  \end{itemize}
\item
  \href{https://www.unrealengine.com/en-US/blog/realityscan-is-now-free-to-download-on-ios}{Reality
  Scan}
\item
  \href{https://www.youtube.com/watch?v=CEC5UwPV9gY}{Drone SLAM}
\item
  \href{https://www.substance3d.com/}{Adobe substance3d}
\item
  \href{https://3dpresso.ai/viewer?seq=mr3.yg5isic8KGJZ1DAjW5VMc}{3DPresso}
\item
  \href{https://machinelearning.apple.com/research/pointersect}{Apple
  point cloud rendering}
\item
  Roblox

  \begin{itemize}
   
  \item
    \href{https://techcrunch-com.cdn.ampproject.org/c/s/techcrunch.com/2022/09/09/roblox-rdc-2022/amp/}{Campus}
  \end{itemize}
\item
  Vircadia
\item
  O3DE

  \begin{itemize}
   
  \item
    \href{https://www.reddit.com/r/O3DE/comments/pbovl9/can_i_develop_my_own_dedicated_server_with_o3de/}{server}
  \item
    \href{https://www.co3dex.com/blog/image-based-lighting-1/\#/}{Global
    lighting}
  \end{itemize}
\item
  Unreal
\item
  \href{https://www.matthewball.vc/all/forwardtothemetaverseprimer}{Technically
  this might be a decade away since like everything the primay user base
  will be mobile mixed realitym, which is contingent on 5G}
\item
  \href{https://www.matthewball.vc/all/why-vrar-gets-farther-away-as-it-comes-into-focus}{the
  many challenges of XR hardware}
\item
  MoveAI
\item
  \href{https://www.from-the-interface.com/wrist-interfaces/}{Metaquotesingle s
  wrist reader}
\item
  \href{https://scitechdaily.com/groundbreaking-new-technology-allows-people-to-listen-to-music-through-touch/}{Touch
  music interface}
\item
  Interface and tracking

  \begin{itemize}
   
  \item
    Pose estimations

    \begin{itemize}
     
    \item
      \href{https://www.standablevr.com/}{Standable}
    \end{itemize}
  \item
    \href{https://microsoft.github.io/DenseLandmarks/}{Dense face fields
    from Microsoft}
  \end{itemize}
\item
  Viveverse web3 nonsense
\item
  \href{https://medium.com/@ElizAyer/meetings-are-the-work-9e429dde6aa3}{Meetungs
  ARE the work}
\item
  \href{https://venturebeat.com/virtual/identity-in-the-metaverse-creating-a-global-identity-system/}{Strongnode
  identity article on venturebeat}
\item
  legal / governance / privacy / safeguarding

  \begin{itemize}
   
  \item
    legal jeopardy for celebrities
  \item
    \href{https://www.smashingmagazine.com/printed-books/understanding-privacy/\#bookTOC}{Privacy
    law book}
  \item
    \href{https://webdevlaw.uk/2022/11/21/a-quick-hypothetical-situation-or-your-crash-introduction-to-the-real-world/}{Online
    safety bill heather articles}
  \item
    \href{https://www.vice.com/en/article/3abpg3/woman-says-she-was-virtually-gang-raped-in-facebooks-metaverse?}{Gang
    sexual assault vice article}
  \item
    \href{https://www.thecable.ng/safeguarding-africans-safety-and-freedom-in-the-metaverse/amp}{not
    enough training on safety in africa}
  \item
    \href{https://techcrunch.com/2021/12/21/borderless-crypto-networks-wrestle-with-state-sanction-compliance/?}{Techcrunch
    on borderless payments}
  \item
    \href{https://www.forbes.com/sites/nisaamoils/2023/03/01/how-regulation-will-apply-to-the-metaverse/?}{How
    Regulation Will Apply To The Metaverse}
  \item
    \href{https://www.simpleanalytics.com/blog/norway-takes-a-stance-against-google-analytics}{Norway
    takes a stance against Google Analytics}
  \item
    \href{https://www.bigtechnology.com/p/social-media-is-changing-and-paid}{Social
    Media Is Changing, And Paid Accounts Are The Response}
  \item
    \href{https://www.reply.com/en/metaminutes-s3-e5-legal-challenges-and-regulation-for-the-metaverse}{Podcast
    on the law}
  \end{itemize}
\item
  \href{https://github.com/nglviewer/ngl}{NGL protein fold model viewer}
\item
  \href{discord.gg/AMRdyPjwBb}{OpenBioML discord}
\item
  \href{https://www.youtube.com/watch?v=Q-V5EQ-FBMc}{Nanome on quest
  pro}
\item
  \href{https://github.com/aqlaboratory/openfold}{Openfold github}
\item
  \href{https://github.com/schrodinger/pymol-open-source}{Pymol2 open
  source visualisation}
\item
  Alphafold OpenAI

  \begin{itemize}
   
  \item
  \end{itemize}
\item
  \href{https://github.com/RosettaCommons/RFdiffusion}{Biological
  structure diffusion}

  \begin{itemize}
   
  \item
    The RFdiffusion code allows for the running of RFdiffusion
    simulations. The code is written in Python and is available on
    GitHub. The code includes a number of features, such as the ability
    to run simulations on multiple processors and the ability to output
    results in a variety of formats.
  \end{itemize}
\item
  \href{https://www.amazon.co.uk/AI-Revolution-Medicine-GPT-4-Beyond/dp/0138200130}{Diagnostics}
\item
  \href{https://www.adidas.com/into_the_metaverse/mint}{Addidas}
\item
  \href{https://www.bubblepunk.io/bubblepunk-interiors}{Bubblepunk
  interiors ML art}
\item
  \href{https://www.bloomberg.com/news/articles/2022-09-22/what-is-a-chief-metaverse-officer-and-do-you-need-one}{What
  is a chief metaverse officer (bloomberg)}
\item
  \href{https://www.coindesk.com/markets/2022/04/06/metaverse-majors-struggle-as-user-base-falls-short-of-market-expectations/?outputType=amp}{Userbase
  struggles (coindesk)}
\item
  \href{https://wwd.com/business-news/technology/metaverse-lawsuit-nike-stockx-hermes-metabirken-fashion-1235247763/}{Protecting
  Brands in the Metaverse's Uncertain Legal Landscape}
\item
  \href{https://www.analysisgroup.com/globalassets/insights/publishing/2022-the-potential-global-economic-impact-of-the-metaverse.pdf}{Market
  research global impact}
\item
  \href{https://www.businessinsider.com/mcdonalds-metaverse-virtual-online-restaurant-trademark-delivers-food-web3-nft-2022-2}{McDonalds
  in the metaverse}
\item
  \href{https://www.musicweek.com/labels/read/universal-music-group-s-digital-strategy-team-creates-key-roles-for-web3-and-the-metaverse/087103}{Universal
  music metaverse / web3 team}
\item
  \href{https://www.epsilontheory.com/narrative-and-metaverse-pt-3-the-luther-protocol/\#.YjyHbnLIE5k.twitter}{With
  the help of generative AI it may be possible to democratise the
  externalisation of complex narratives, with these new narratives
  shaping the outcomes of society through the medium of the metaverse}
\item
  \href{https://thedriven.io/2022/05/23/nissan-and-mitsubishi-unveil-electric-mini-vehicles-and-test-drives-in-metaverse/}{A
  lot of metaverse recently has just been convergence as companies take
  their existing simulation and repackage it for the moment.}
\item
  Games is the main convergence: from globalblock ""More companies are
  entering the metaverse as global electronics giant Sony has announced
  their own metaverse push in the latest annual corporate strategy
  meeting. Sony said this will be a more focused approach, as they aim
  to use metaverse-inspired experiences to engage users. As Sony owns
  PlayStation Brands, one of the biggest install userbases in the world,
  they are in an amazing position to make an impact. They have also
  revealed that prior investments in Epic, makers of the Fortnite game,
  and Bungie, another gaming studio, are part of this push."

  \begin{itemize}
   
  \item
  \end{itemize}
\item
  \href{https://www.epsilontheory.com/narrative-and-metaverse-pt-3-the-luther-protocol/\#.YjyHbnLIE5k.twitter}{Epsilomn
  theory thesis on metaverse}
\item
  \href{https://www.geekmetaverse.com/epic-games-launches-verse-the-metaverse-programming-language/}{Epic
  games programming language for the metaverse}
\item
  \href{https://www.ign.com/articles/how-fortnite-is-the-antidote-to-metaverse-skepticism}{Fortnite
  is the metaverse}

  \begin{itemize}
   
  \item
    \href{https://store.epicgames.com/en-US/p/fortnite--uefn?}{epic
    unreal for fortnite}
  \end{itemize}
\item
  Why you should use now generative AI in your metaverse company. Or
  maybe not - The Ghost Howls
  https://skarredghost.com/2023/02/11/generative-ai-metaverse-company/
\item
  BlackRock digs further into crypto with metaverse ETF
  https://financefeeds.com/blackrock-digs-further-into-crypto-with-metaverse-etf/
\item
  China's iPhone production hub of Henan bets its future on the
  metaverse bar{} South China Morning Post
  https://www.scmp.com/tech/policy/article/3194092/chinas-iphone-production-hub-henan-bets-its-future-metaverse
\item
  Cutting Through the Hotel Hype of the Blockchain, Web3 and the
  Metaverse bar{}
  https://hoteltechnologynews.com/2022/08/cutting-through-the-hotel-hype-of-the-blockchain-web3-and-the-metaverse/
\item
  Experts highlight trust and safety practices for the metaverse
  https://www.techtarget.com/searchcio/news/252525336/Experts-highlight-trust-and-safety-practices-for-the-metaverse
\item
  Global Metaverse Market Analysis Report 2022: Blockchain
  https://www.globenewswire.com/news-release/2022/08/30/2506629/0/en/Global-Metaverse-Market-Analysis-Report-2022-Blockchain-Solutions-in-Support-of-the-Metaverse-Market-will-Reach-148-6-Billion-by-2027.html
\item
  Identity Management Institute Launches the Metaverse Security Center
  and Certified Metaverse Security Consultant (CMSC)  Certification
  https://www.prnewswire.com/news-releases/identity-management-institute-launches-the-metaverse-security-center-and-certified-metaverse-security-consultant-cmsc-certification-301689276.html
\item
  Is the metaverse good for business? Why blending the virtual and the
  real remains a matter of much debate bar{} Fortune
  https://fortune.com/2022/07/13/business-metaverse-dropbox-brainstorm-tech/
\item
  Laws and Issues in the Metaverse (2) - Lexology
  https://www.lexology.com/library/detail.aspx?g=5a0cc4c0-a876-474e-a719-f528b71b68ee
\item
  Laying the Foundation of the Metaverse, Streaming Video, Social,
  Gaming, and Broader Digital Advertising Markets to Collectively Clear
  US\$2 Trillion by 2030
  https://www.abiresearch.com/press/laying-the-foundation-of-the-metaverse-streaming-video-social-gaming-and-broader-digital-advertising-markets-to-collectively-clear-us2-trillion-by-2030/
\item
  Major crypto exchange announces its arrival in the metaverse
  https://cointelegraph.com/news/major-crypto-exchange-announces-its-arrival-in-the-metaverse
\item
  Metaverse exploitation and abuse to rise in 2023: Kaspersky
  https://cointelegraph.com/news/metaverse-exploitation-and-abuse-to-rise-in-2023-kaspersky
\item
  Metaverse Market Size, Share \& Industry Report 2020-2030
  https://www.strategicmarketresearch.com/market-report/metaverse-market
\item
  Metaverse Real Estate Gets Reality Check
  https://therealdeal.com/2022/08/04/metaverse-real-estate-gets-reality-check/
\item
  Nissan and Mitsubishi unveil electric mini vehicles, and test drives
  in metaverse
  https://thedriven.io/2022/05/23/nissan-and-mitsubishi-unveil-electric-mini-vehicles-and-test-drives-in-metaverse/
\item
  Nvidia Sees a Metaverse Populated With Lifelike Chatbot Avatars - CNET
  https://www.cnet.com/tech/computing/nvidia-sees-a-metaverse-populated-with-lifelike-chatbot-avatars/
\item
  Roomquotesingle{} Offers a Non-Facebook Way to Connect Coworkers
  in the Metaverse
  https://uk.pcmag.com/vr-1/143198/room-offers-a-non-facebook-way-to-connect-coworkers-in-the-metaverse
\item
  The Architecture of the Metaverse (So Far) bar{} ArchDaily
  https://www.archdaily.com/988639/the-architecture-of-the-metaverse-so-far
\item
  The battle to build a child-friendly metaverse bar{} Tech News
  https://tech.hindustantimes.com/tech/news/the-battle-to-build-a-child-friendly-metaverse-71655616713236.html
\item
  The Metaverse Casino That Wasn't
  https://www.coindesk.com/layer2/sinweek/2022/08/29/the-metaverse-casino-that-wasnt/
\item
  The Worldquotesingle s First Virtual Reality Avatar Fashion Week
  Is On The Metaverse This Week
  https://womenlovetech.com/the-worlds-first-virtual-reality-avatar-fashion-week-is-on-the-metaverse-this-week/
\item
  Top 10 Metaverse Platforms that will Replace Social Media in Future
  https://www.analyticsinsight.net/top-10-metaverse-platforms-that-will-replace-social-media-in-future/
\item
  Top 15 Metaverse Companies To Watch Out For !!
  https://www.cryptotimes.io/top-15-metaverse-companies-to-watch-out-for/
\item
  Wequotesingle re Ready for the Metaverse but the Technology Is
  Not. Herequotesingle s Why. - Decrypt
  https://decrypt.co/100781/were-ready-for-the-metaverse-but-the-technology-is-not-heres-why
\item
  \href{https://cornerstone.land/}{The Photorealistic Metaverse
  bar{} Welcome to Cornerstone, Cornerstone is a gamified metaverse
  experience distributed to you via the web browser. Create, co-develop,
  and monetize your creative idea in the new digital realm.}
\item
  \href{https://gadgets.ndtv.com/cryptocurrency/news/mega-yacht-sold-usd-650000-metaverse-most-expensive-nft-sandbox-virtual-world-2630187}{Mega
  Yacht Sold for \$650,000 in Metaverse, Becomes Most-Expensive NFT in
  Sandbox Virtual World bar{} Technology News , A mega yacht has
  been sold for a whopping \$650,000 (roughly Rs. 4.8 crore) in the
  Sandbox virtual gaming world. The pricey digital asset was released by
  metaverse developer Republic Realm as part of a luxury NFT series.}
\item
  \href{https://cointelegraph.com/news/facebook-whistleblower-warns-metaverse-will-repeat-the-harms}{Facebook
  whistleblower warns Metaverse will repeat `all the harms',Frances
  Haugen says she is worried about privacy and safety inside Meta's
  impending Metaverse. Her accusations of profit before safety are still
  red hot.}
\item
  \href{https://virtualproducer.io/generative-ai-and-the-future-of-filmmaking/}{Virtual
  production and the future of generative art}
\item
  \href{https://www.thestreet.com/technology/mark-zuckerberg-quietly-buries-the-metaverse}{Zuckerburg
  disengages from metaverse}
\item
  \href{https://labusinessjournal.com/featured/metahouse-could-be-first-of-many/}{Metahouse
  Could be First of Many - Los Angeles Business Journal digital twin of
  a mansion}
\item
  \href{https://www.youtube.com/watch?v=EiZhdpLXZ8Q}{The Future is a
  Dead Mall - Decentraland and the Metaverse: Clickbait Title: I spent
  three months living in the metaverse and now Iquotesingle m
  starvingThe metaverse salespeople have a weird fixation with Animal
  Crossing, in sp...}
\item
  https://www.infosys.com/iki/perspectives/metaverse-insider-guide.html
\item
  \href{https://www.reddit.com/r/CryptoCurrency/comments/128hqkw/meta_microsoft_and_disney_are_reversing_their/}{Everyone
  abandoning metaverse}
\item
  \href{https://www.wired.com/story/metaverse-ethics/}{The Internet Is
  Ruined. The Metaverse Can Still Be Saved: In this nascent stage, there
  are opportunities for virtual worlds to avoid the mistakes of the
  past.}
\item
  \href{https://sociable.co/government-and-policy/wef-global-risks-report-cyber-pandemic-erosion-trust-social-cohesion/}{WEF
  risks report links}
\item
  Regulation (everything)

  \begin{itemize}
   
  \item
    Crypto

    \begin{itemize}
     
    \item
      \href{https://www.gov.uk/government/news/uk-sets-out-plans-to-regulate-crypto-and-protect-consumers}{UK}
    \end{itemize}
  \end{itemize}
\item
  \href{https://arxiv.org/abs/2303.10130}{GPTs are GPTs: An Early Look
  at the Labor Market Impact}
\item
  \href{https://www.imf.org/en/News/Articles/2023/02/10/el-salvador-staff-concluding-statement-of-the-2023-article-iv-mission}{El
  Salvador: Staff Concluding Statement of the 2023 Article IV Mission
  (other)}
\item
  \href{https://ir.silvergate.com/news/news-details/2022/Silvergate-Purchases-Blockchain-Payment-Network-Assets-from-Diem/default.aspx}{Silvergate
  Purchases Blockchain libre}
\item
  \href{https://www.technologyreview.com/2022/04/06/1048981/worldcoin-cryptocurrency-biometrics-web3/}{Deception,
  exploited workers, and cash handouts: How Worldcoin recruited its
  first half a million test users: The startup promises a
  fairly-distributed, cryptocurrency-based universal basic income. So
  far all itquotesingle s done is build a biometric database from
  the bodies of the poor.}
\item
  \href{https://blogs.nvidia.com/blog/2022/01/04/omniverse-available-free-to-creators/}{Free
  to individuals}
\item
  \href{https://www.youtube.com/watch?v=Jm155QkRjl0\&feature=youtu.be}{Full
  RTX rendering}
\item
  \href{https://blogs.nvidia.com/blog/2023/02/15/blender-alpha-release-omniverse/?ncid=so-link-466434\#cid=ov01_so-link_en-us}{AI
  assisted blended character plugin}
\item
  \href{https://blogs.nvidia.com/blog/2022/08/09/omniverse-siggraph/}{NVIDIA
  Unveils Powerful AI, Simulation and Creative Tools for Creators and
  Developers of Virtual Worlds bar{} NVIDIA Blog}
\item
  \href{https://discord.gg/openmetaverse}{Open metaverse discord from
  linux foundation}
\item
  \href{https://huggingface.co/datasets/allenai/objaverse}{Free 1
  Million objects}
\item
  weyl2022decentralized
\item
  -Compensating coordinated strategic behavior -Measuring
  decentralization -Creating novel markets with decomposable, shared
  rights \& permissions                         Souls can be used as a
  natural way for artists to stake their reputation on their works. When
  issuing an NFT, an artist can issue it from their Soul. pastry By
  viewing the SBTs in an artist's Soul, buyers can confirm the Soul
  belongs to the artist, thereby confirming the NFTs legitimacy.
  Additionally, artists could issue an SBT in their Soul that attests to
  the NFT's membership to a collection \& vouches for its scarcity.
  Souls would thus create a verifiable, on-chain way to stake and build
  reputation on the provenance and scarcity of an object. This can go
  beyond art. Souls can be used for services, rentals, and any market
  built on scarcity, reputation, or authenticity. There is no method for
  establishing reputation for web3 identities. SBTs that represent
  education credentials, work history, previous loans, and rental
  contracts could serve as a persistent record of credit relevant
  history.                                             So far, web3 has
  largely relied on token sales or airdrops to summon new communities.
  SBTs offer a radical improvement called ``souldrops''. Using SBTs, a
  DAO that wants to form a community within a specific L1 can souldrop
  to devs who hold 3/5 conference attendance SBTs, or other tokens
  reflecting attendance like POAPs.
\item
  \href{https://www.businessinsider.com/mcdonalds-metaverse-virtual-online-restaurant-trademark-delivers-food-web3-nft-2022-2}{bridging
  the real and the virtual like mcdonalds home delivery}
\item
  virtual
\item
  \href{https://labusinessjournal.com/featured/metahouse-could-be-first-of-many/}{hybrid
  land linking real and virtual (including digital twin)}
\item
  Simple geo-referencing of physical place in mixed reality
\item
  \href{https://multion.ai/}{MultiOn digital assistant}
\item
  \href{https://docs.getleon.ai/}{LEON open source assistant}
\item
  \href{https://github.com/LAION-AI/Open-Assistant/issues}{Open source
  assistant github of issues}
\item
  \href{https://vrcmods.com/}{Free VRChat Models \& Avatars bar{}
  VRCMods (other)}
\item
  \href{https://clip-actor.github.io/}{CLIP-Actor Text-Driven
  Recommendation and Stylization for Animating Human Meshes}
\item
  \href{https://github.com/inferno-os/inferno-os}{Inferno is a
  distributed operating system which uses a file-like name hierarchy to
  represent services and resources, including devices, network and
  protocol interfaces, dynamic data sources, and services.Applications
  are written in a concurrent programming language, Limbo.}
\item
  What is a predictive metaverse? The future of guided learning
  https://www.eschoolnews.com/educational-leadership/2023/04/21/predictive-metaverse-the-future-of-guided-learning/
\item
  \href{https://www.reddit.com/r/virtualreality/comments/12rro32/meta_ai_proposed_an_algorithmbased_arvr_body/}{Meta
  proposal to infer for advertising from movement}
\item
  \href{https://www.reddit.com/r/vfx/comments/12ok0xe/how_to_scan_environments_for_free_without_any/}{Scan
  outdoor environments using stock images}
\item
  \href{https://www.reddit.com/r/CryptoCurrency/comments/128hqkw/meta_microsoft_and_disney_are_reversing_their/}{Meta
  and disney dropping metaverse}
\item
  \href{https://www.arible.co/prompts}{Arible Avatars \& Virtual Studio:
  Professional Photography Without Photographers Or The Camera:
  Unlimited Realistic or Artistic photos of yourself and others monthly}
\item
  \href{https://www.wired.com/story/metaverse-ethics/}{The article
  discusses how the internet has ruined the metaverse, and how it can
  still be saved. It argues that the internet has made the metaverse
  less accessible and more difficult to navigate, and that this has had
  a negative impact on its potential. The article suggests that the
  metaverse can still be saved if we take steps to improve its
  accessibility and make it easier to use.}
\item
  \href{https://www.bbntimes.com/technology/exploring-why-the-metaverse-hasn-t-taken-off-as-expected}{Exploring
  Why the Metaverse Hasnquotesingle t Taken Off as Expected: The
  metaverse has quickly turned from a profitable utopia into a
  cash-guzzling dystopia.The text provides an overview of the Metaverse,
  a virtual world that has not yet taken off as expected. The text
  describes the potential reasons for this, including the lack of a
  clear business model and the difficulty of creating an immersive
  experience.}
\item
  \href{https://www.reddit.com/r/virtualreality/comments/12lpsvf/rumor_meta_quest_had_more_than_6_million_monthly/}{6
  million meta VR users, against 60B spent}
\item
  \href{https://www.bloomberg.com/news/articles/2023-04-14/meta-urged-to-halt-plans-allowing-minors-into-the-metaverse?leadSource=uverify\%20wall}{Meta
  urged to prevent children in metaverse}
\item
  \href{https://docs.depthkit.tv/docs/remote-livestreaming-with-webrtc}{Depthkit
  live webrtx streaming for Unity}
\item
  \href{https://www.massmux.com/howto-complete-lightningtipbot-lnbits-setup-vps/}{Setup
  lnbits and lightningtipbot}
\item
  \href{https://github.com/ln-vortex/ln-vortex}{GitHub -
  ln-vortex/ln-vortex: Lightning and Taproot enabled collaborative
  transactions (other)}
\item
  \href{https://rgb.tech/?ref=nobsbitcoin.com}{RGB is a smart contract
  platform that is scalable, private, and interoperable with Bitcoin and
  Lightning Network. It is possible to issue assets, create NFTs, and
  run DAOs on RGB.}
\item
  \href{https://github.com/lncapital/torq}{This is a node management
  software for large Lightning Network nodes. It provides a way to
  automate workflows, manage code changes, and track work progress.}
\item
  \href{https://investorsking.com/2023/03/08/90-million-people-use-cryptocurrency-in-nigeria-reports/}{90
  Million People Use Cryptocurrency in Nigeria - Report bar{}
  Investors King}
\item
  \href{https://www.prnewswire.com/apac/news-releases/2023-independent-reserve-cryptocurrency-index-shows-singaporeans-are-still-actively-investing-in-crypto-despite-hit-in-overall-confidence-301783400.html}{2023
  Independent Reserve Cryptocurrency Index shows Singaporeans are still
  actively investing in crypto despite hit in overall confidence:
  /PRNewswire/ -\/- In the latest study{[}1{]} by Independent Reserve,
  Singaporequotesingle s first regulated cryptocurrency exchange
  for all investors, Singaporeans{[}2{]} are still...}
\item
  \href{https://bitnob.com/blog/how-to-buy-and-sell-bitcoin-in-nigeria}{Bitnob
  African exchange}
\item
  \href{https://bitcoinmagazine.com/business/bitcoin-entrepreneurs-introduce-noones-app-aimed-at-empowering-financial-freedom}{Noones
  peer2peer for Africa}
\item
  \href{https://twitter.com/documentingbtc/status/1646656229958361091}{Africa
  leads the world in peer to peer bitcoin}
\item
  Bitcoin

  \begin{itemize}
  \item
    \href{https://dergigi.com/2021/12/30/the-freedom-of-value/}{The
    Freedom of Value - How Value-for-Value Fixes the Monetization of
    Information bar{} dergigi.com,Thoughts about Bitcoin and other
    things.}
  \item
    http://bitcoin secure multisig setup (bsms 2 file\_get\_contents():
    php\_network\_getaddresses: getaddrinfo failed: Name or service not
    known 2 file\_get\_contents(http://bitcoin secure multisig setup
    (bsms): failed to open stream: php\_network\_getaddresses:
    getaddrinfo failed: Name or service not known
  \item
    \begin{itemize}
     
    \item
      \url{https://bitcoinmagazine.com/legal/u-s-treasury-introduces-cbdc-digital-dollar-working-group}
    \end{itemize}
  \item
    \href{https://www.msn.com/en-us/money/news/crypto-wave-gaining-momentum-in-germany-network-of-1-200-banks-to-offer-bitcoin/ar-AA198Lxc}{Crypto
    Wave Gaining Momentum In Germany: Network Of 1,200 Banks To Offer
    Bitcoin: Deutsche WertpapierService Bank (Dwpbank), a provider of
    securities processing to approximately 1,200 banks in Germany, plans
    to launch a new platform called wpNex. This platform will offer
    Bitcoin access to all affiliated retail customers in the latter half
    of 2023. The innovative service will integrate cryptocurrency
    accounts with customersquotesingle{} existing bank accounts,
    bypassing the need for additional Know Your Customer procedures,
    local media...}
  \item
    https://www.cointime.com/news/hal-finneys-theory-of-bitcoin-backed-banks-74474
  \item
    \href{https://braiins.com/blog/bitcoin-mining-analogy-beginners-guide}{bitcoin-mining-analogy-beginners-guide}
  \item
    \href{https://medium.com/vinteum-org/introducing-floresta-an-utreexo-powered-electrum-server-implementation-60feba8e179d}{Introducing
    Floresta, a Utreexo-powered Electrum Server implementation: Bitcoin
    is a groundbreaking technology that enables users worldwide to
    transfer value in a trustless and borderless manner. Bitcoin's
    core\ldots{}}
  \item
    \href{https://www.whitehouse.gov/wp-content/uploads/2023/03/ERP-2023.pdf}{New
    critical white house report}
  \item
    \href{https://www.nobsbitcoin.com/fedimint-hackathon-winners-announced/}{Fedimint
    Hackathon Winners Announced: 2.58 BTC in Prizes: "The quality of the
    modules that were submitted was truly impressive, with projects from
    federated storage to community finance tools that really highlighted
    the potential impact of Fedimint as a platform that could solve
    real-world problems."}
  \item
    https://geometry.xyz/notebook/A-light-introduction-to-ZeroSync
  \item
    \href{https://www.technologyreview.com/2022/04/06/1048981/worldcoin-cryptocurrency-biometrics-web3/}{Deception,
    exploited workers, and cash handouts: How Worldcoin recruited its
    first half a million test users: The startup promises a
    fairly-distributed, cryptocurrency-based universal basic income. So
    far all itquotesingle s done is build a biometric database from
    the bodies of the poor.}
  \item
    \href{https://github.com/ngutech21/cashu-rs}{Cashu rust
    implementation}
  \item
    \href{https://zerosync.org/}{Zerosync bitcoin rollup proofs}
  \end{itemize}
\item
  Mining and energy
\item
  \href{https://www.reddit.com/r/CryptoCurrency/comments/12xu714/bitcoin_has_just_surpassed_sweden_for_overall/}{Bitcoin
  uses more energy than sweden}
\item
  \href{https://twitter.com/satoshiactfund/status/1648445448833875969}{THE
  quotesingle RIGHT TO MINEquotesingle{} \#BITCOIN  IS NOW
  LAW IN THE STATE OF ARKANSAS!}
\item
  \href{https://www.linkedin.com/posts/danielsbatten_like-evs-bitcoin-is-a-fully-electrified-activity-7049321186605858816-t4MB?utm_source=share\&utm_medium=member_android}{Bitcoin
  is a more sustainable energy than EVs, and significantly less fossil
  fuel.}
\item
  Digital objects
\item
  In games

  \begin{itemize}
   
  \item
    \href{https://twitter.com/DrDisrespect/status/1632430208379928576}{DrDisrespect
    tweet}
  \item
    \href{https://github.com/beamable/genamon-polygon/}{Polygon
    generative art game}
  \end{itemize}
\item
  \href{https://docsend.com/view/he8x9erkjmphphvn}{RGB explainer slides}

  \begin{itemize}
   
  \item
    \href{https://twitter.com/iris_wallet/status/1639189676845047808}{rgb
    tokens}
  \item
    \href{https://t.me/rgbtelegram/36013}{RGB minimal fork for tether}
  \item
    \href{https://play.google.com/store/apps/details?id=com.iriswallet.testnet}{Iris
    wallet}
  \item
    \href{https://diba.io/}{Diba wallet and marketplace}
  \end{itemize}
\item
  \href{https://bitcoinist.com/the-numbers-inscriptions-affect-bitcoin-blocksize/}{By
  The Numbers: How Do Inscriptions Affect Bitcoin Blocksize: Bitcoin
  Inscriptions have increased the average size of the
  cryptocurrencyquotesingle s blocks; herequotesingle s how
  this could impact the blockchain.}
\item
  \href{https://bitcoinist.com/uk-government-scraps-nft-launch-plan-for-now/}{UK
  Government Scraps NFT Launch Plan For Now: UK government had unveiled
  its intention to introduce its very own NFTs through the Royal Mint.
  This announcement was made last year in April.}
\item
  \href{https://openordex.org/}{OpenOrdex is a decentralized exchange
  for ordinal numbers. It allows users to buy and sell ordinal numbers
  using a variety of methods, including Inscription, which is a process
  by which users can add their own numbers to the exchange.}
  \begin{itemize}
  \item
  \end{itemize}
\item
  Stablecoins and CBDCs
\item
  \href{https://bitcoinke.io/2022/07/latin-america-in-mastercard-new-payments-index-2022/}{Over
  1/3 Made a Purchase in Stablecoins in Latin America, Says Latest
  MasterCard New Payments Index 2022: Reporting on Fintech, Crypto, and
  Blockchain Activity in Africa}
\item
  \begin{itemize}
   
  \item
    \url{https://bitcoinmagazine.com/legal/u-s-treasury-introduces-cbdc-digital-dollar-working-group}
  \end{itemize}
\item
  rbi monetary museum: Indiaquotesingle s e-rupee unpopular as
  central banks push digital currency - The Economic Times
  https://economictimes.indiatimes.com/industry/banking/finance/banking/indias-e-rupee-unpopular-as-central-banks-push-digital-currency/articleshow/99049236.cms?from=mdr
\item
  \href{https://www.nobsbitcoin.com/kollider-wallet/}{Kollider Wallet:
  Browser-based Lightning \& Nostr Extension: Kollider is a new
  custodial Lightning + Nostr wallet with native stablecoin
  integration.}
\item
  \href{https://www.atlanticcouncil.org/cbdctracker/}{The Current List
  of CBDCs In Development Around the World}
\item
  Fantastical NeRFs

  \begin{itemize}
  \item
    \href{https://neuralradiancefields.io/history-of-neural-radiance-fields/}{History
    of NeRFs}
  \item
    waiting on capture
  \item
    \href{https://www.matthewtancik.com/nerf}{Nerfs}
  \item
    \href{https://github.com/sxyu/volrend}{viewier}
  \item
    Windows NeRF environment to WebGL

    \begin{itemize}
     
    \item
      \href{https://github.com/bycloudai/instant-ngp-Windows}{install
      windows NeRF}
    \end{itemize}
  \item
    check out mip nerf 360s
  \item
    \href{https://github.com/marek-simonik/record3d_unity_streaming}{Record3D}
  \item
    \href{https://github.com/yenchenlin/awesome-NeRF}{github of links}
  \item
    \href{https://www.linkedin.com/posts/robcsloan_nerfstudio-nerfstudio-polycam-activity-6999169160379297792-SN4F?utm_source=share\&utm_medium=member_desktop}{nerfs
    with polycam}

    \begin{itemize}
     
    \item
      \href{https://docs.nerf.studio/en/latest/quickstart/custom_dataset.html\#polycam-capture}{Polycam
      developer mode instructions}
    \end{itemize}
  \item
    \href{https://elicit3d.github.io/}{Nerf to animated people oneshot}
  \item
    \href{https://paperswithcode.com/paper/4k-nerf-high-fidelity-neural-radiance-fields}{4K
    ultra high res nerfs with code}

\begin{itemize}
     
    \item
      \href{https://github.com/frozoul/4K-NeRF}{code}
    \end{itemize}
  \item
    \href{https://www.reddit.com/r/deeplearning/comments/zowgqn/neural_rendering_reconstruct_your_city_in_3d/}{city
    modelling}
  \item
    \href{https://waymo.com/research/block-nerf/}{more city modelling}
  \item
    \href{https://github.com/3a1b2c3/seeingSpace/wiki/Hands-on:-Getting-started-and-Nerf-frameworks}{field
    guide}
  \item
    \href{https://github.com/ToniRV/NeRF-SLAM}{NeRF SLAM}
  \item
    \href{https://www.xxlong.site/NeuralUDF/}{NeuralUDF surface capture}
  \item
    \href{https://arxiv.org/abs/2102.06205}{stablisation paper}
  \item
    \href{https://alexyu.net/plenoxels/}{nerfs without neural nets}
  \item
    \href{https://vcai.mpi-inf.mpg.de/projects/NeuS2/}{NeuS2: Fast
    Learning of Neural Implicit Surfaces for Multi-view Reconstruction}
  \item
    \href{https://www.matthewtancik.com/nerf}{Original 2020 nerf paper}
  \item
    \href{https://sites.google.com/view/recolornerf?pli=1}{Recolour
    NeRF}
  \item
    \href{https://volinga.ai/}{Volinga Nerf into Unreal}
  \item
    \href{https://make-a-video3d.github.io/}{Text2Nerf4D}
  \item
    \href{https://robustnerf.github.io/public/}{Robust nerfs which deal
    with occlusion}
  \item
    \href{https://github.com/JamesPerlman/NeRFRenderCore/blob/main/src/integrations/blender.cuh}{Blender
    integration}
  \item
    \href{https://github.com/NVlabs/instant-ngp\#vr-controls}{Rapidnerf
    VR integration with erase}
  \item
    \href{https://bakedsdf.github.io/}{Nerf to large scale geom}
  \item
    \href{https://elicit3d.github.io/}{ELICIT,ELICIT creates
    free-viewpoint motion videos from a single image by constructing an
    animatable NeRF representation in one-shot learning. Offcial website
    of quotesingle One-shot Implicit Animatable Avatars with
    Model-based Priorsquotesingle{}}
  \item
    \href{https://github.com/frozoul/4k-nerf}{GitHub - frozoul/4K-NeRF:
    Official implementation of arxiv paper 4K-NeRF: High Fidelity Neural
    Radiance Fields at Ultra High Resolutions , Official implementation
    of arxiv paper 4K-NeRF: High Fidelity Neural Radiance Fields at
    Ultra High Resolutions - GitHub - frozoul/4K-NeRF: Official
    implementation of arxiv paper 4K-NeRF: High Fidelity Neural Radiance
    Fields at Ultra High Resolutions}
  \item
    \href{https://climatenerf.github.io/}{ClimateNeRF,-}
  \item
    \href{https://github.com/tonirv/nerf-slam}{GitHub -
    ToniRV/NeRF-SLAM: NeRF-SLAM: Real-Time Dense Monocular SLAM with
    Neural Radiance Fields.}
  \item
    \href{https://grail.cs.washington.edu/projects/humannerf/}{HumanNeRF:
    Free-viewpoint Rendering of Moving People from Monocular
    Video,HumanNeRF: Free-viewpoint Rendering of Moving People from
    Monocular Video}
  \item
    \href{https://instruct-nerf2nerf.github.io/}{editing nerfs with
    instructions}

    \begin{itemize}
     
    \item
      \href{https://mobile.twitter.com/bilawalsidhu/status/1638919452392583169}{instruct2nerf
      twitter thread}
    \end{itemize}
  \item
    \href{https://github.com/taichi-dev/taichi-nerfs}{Render without
    cuda using just pytorch}
  \item
    \href{https://totoro97.github.io/projects/f2-nerf/}{Nerf with free
    camera trajectory}
  \item
    \href{https://www.lerf.io/}{Language embedded nerfs (LERFS)}
  \item
    \href{https://repo-sam.inria.fr/fungraph/3d-gaussian-splatting/}{Splatting
    paper, go where you like}
  \item
    \href{https://github.com/lyclyc52/NeRF_RPN}{nerf RPN}
  \end{itemize}
\end{itemize}


