\section{Global politics \& digital society}
Austerity is a term used to describe a set of economic policies that aim to reduce government spending and debt, often through cuts to public services and welfare programs. The concept of austerity has its origins in the 1920s, following the end of World War I and the economic crisis that ensued. In the wake of the war, many Western European countries were struggling with high levels of debt and inflation. In response, governments began implementing policies to reduce spending and balance their budgets.\par
We have seen in the previous chapter that the concept of inflation itself is complex, and somewhat argued about still. In the 1920s, Keynes was one of the first to argue against austerity measures, arguing that cutting government spending during a recession would only worsen the economic downturn. Instead, he advocated for increased government spending to stimulate economic growth and reduce unemployment. Despite this, many governments continued to implement austerity policies throughout the 1920s and 1930s.\par
In the post-World War II period, the rise of the welfare state and the adoption of Keynesian economic policies led to a shift away from austerity in many countries. However, in the 1970s, a new economic crisis led to a resurgence of austerity policies, particularly in the United States and United Kingdom. In the 1980s, the rise of neoliberalism and the influence of economists such as Milton Friedman led to further cuts to government spending and the rolling back of the welfare state.\par 
Today, the concept of austerity continues to shape economic policy, particularly in the wake of the 2008 financial crisis. Many governments, particularly in Europe, have implemented austerity measures in response to the crisis, leading to cuts to public services and welfare programs. The effectiveness of these policies remains a contentious issue, with some arguing that they have helped to reduce debt and stabilize economies, while others argue that they have led to increased inequality and hindered economic growth. Looking around at the state of the world, and the widening gap between the rich and the poor, it is possible to have some sympathy with those who see patterns in the bahaviour of political leaders and the controllers of Western capital and global resources. The system seems engineered to reward a few. It is possible to view `austerity' as a means of political control of economic levers, in order to de-democratise populations. This mantra of `do more, consume less' has perhaps become a defacto methodology to constrain popular ideas, diverting capital back into the hands of incumbents, land owners, and the politically and economically motivated \cite{mattei2022capital}. It seems that the controlling nexus of this political framework globally is the concept of the central bank, unelected technocrats whose tenures span across political administrations. Again, this can be traced back to the 1920's. Hawtrey’s 1925 ``Currency \& Public Administration'' asserts that a central bank should \textit{``Never explain; never regret; never apologise.''}, and speaks glowingly of the selfish market \cite{hawtrey1925currency}. This economic model is referred to as Dirigisme and feels increasingly the global norm \cite{balassa2013theory}.  We can perhaps here see the divergent point at which the lionization of the market began. Again, to be clear, the authors are not economists, but it does seem that in a global digital society there is room to explore more equitable models of global value, governance, and trust.
\subsection{Surveillance Capitalism}
Surveillance capitalism is a term coined by Harvard Business School professor Shoshana Zuboff to describe the business model of using data collected from individuals to target advertising and influence behavior. The concept of surveillance capitalism emerged in the late 20th and early 21st centuries with the rise of technology companies that specialize in gathering and analyzing personal data.\par
The history of surveillance capitalism can be traced back to the early days of the internet. In the 1990s, companies such as DoubleClick and Omniture began collecting data on internet users' browsing habits in order to target advertising. As the internet grew in popularity, these companies were able to gather an increasing amount of data on individuals, allowing them to more effectively target advertising and increase profits.\par
The advent of smart phones and mobile technology in the 2000s further expanded the reach of surveillance capitalism. With the widespread adoption of smart phones and mobile apps, companies were able to collect even more data on individuals, including location data and information about their physical activity. This data was used to target advertising and influence behavior, leading to the rise of companies such as Google and Facebook, which have become dominant players in the digital advertising market.\par
The use of data collected from individuals to influence behaviour has also been used to influence political campaigns. In the 2016 US presidential election, Cambridge Analytica, a data analytics firm, used data collected from Facebook users to influence voter behaviour. The firm used the data to target advertising and create psychological profiles of individuals, allowing them to more effectively influence voter behaviour.\par
The business model of surveillance capitalism has been widely criticized for its ethical implications. Critics argue that the collection and use of personal data without consent is a violation of individuals' privacy and that the use of data to influence behaviour is manipulative and unethical. In recent years, there have been calls for greater regulation of the tech industry to address these concerns.\par 
Surveillance capitalism has led to significant compliance overheads for companies that collect and use personal data. There are a number of laws and regulations that have been put in place to protect individuals' privacy, such as the General Data Protection Regulation (GDPR) in the European Union and the California Consumer Privacy Act (CCPA) in California, USA. These laws require companies to obtain consent from individuals before collecting and using their data, and to provide individuals with the right to access, correct, and delete their data.\par 
Complying with these laws can be costly and time-consuming for companies. They may need to hire additional staff to handle data privacy compliance, and may also need to invest in new technology to manage and protect personal data. In addition, companies are at risk of significant fines if they fail to comply with these laws.\par
In terms of who profits from surveillance capitalism, the primary beneficiaries are technology companies such as Google and Facebook, which have become dominant players in the digital advertising market. These companies collect and analyse large amounts of personal data, which they use to target advertising and influence behavior. This allows them to generate significant profits from advertising revenue.\par
On the other hand, those who suffer the most negative impact from surveillance capitalism are individuals, whose personal data is collected and used without their consent. They are also at risk of their privacy being violated, and their personal data being misused. Additionally, the collection and use of personal data can lead to the manipulation of individuals' behaviour and decision-making, which can have negative consequences for their lives and society at large.\par
Moreover, the business model of surveillance capitalism has also been criticized for creating a power imbalance between companies and individuals. Companies have access to vast amounts of personal data, which they can use to influence behavior and make decisions that affect individuals' lives. This can lead to a lack of privacy and autonomy for individuals, and can also lead to discrimination and bias in decision-making.\par 
This is collectively an erosion of the demarcation between data, state surveillance, banking, and political leadership globally.\par
The term "surveillance state" refers to a state in which government agencies have the power to collect and analyze large amounts of personal data, often without the consent of individuals. The rise of surveillance capitalism has led to concerns about the potential for the creation of a surveillance state, as government agencies may use the data collected by companies for surveillance purposes.\par 
There have been instances where government agencies have used data collected by companies for surveillance purposes. For example, in the United States, the National Security Agency (NSA) has been accused of using data collected by companies such as Google and Facebook for surveillance purposes. The agency's PRISM program, which was revealed by Edward Snowden in 2013, was designed to collect and analyze data from internet companies in order to identify and track individuals. Europe is \href{https://www.patrick-breyer.de/en/posts/chat-control/}{clear about it's intentions} to mandate their complete access to all encrypted personal communications in forthcoming legislation.\par
The use of data collected by companies for surveillance purposes can have significant implications for individuals' privacy and civil liberties. It can also lead to a lack of transparency and accountability, as government agencies may use the data without the knowledge or consent of individuals. In addition, the use of data for surveillance purposes can lead to discrimination and bias in decision-making, as well as a chilling effect on free speech and the exercise of other rights.\par
In conclusion, the rise of surveillance capitalism has led to concerns about the potential for the creation of a surveillance state, as government agencies may use the data collected by companies for surveillance purposes. This can have significant implications for individuals' privacy and civil liberties, and can lead to a lack of transparency and accountability. It's important for laws and regulations to be in place to safeguard citizens' rights and privacy in regards to the use of data by government agencies, and to hold them accountable for any misuse of data, and yet it seems the reality of the situation in `post Snowden' seems far from that.\par 
Surveillance Capitalism. As a quick round-up of this area, which is best researched elsewhere:
\begin{itemize}
\item The global digital advertising market is expected to reach \$335 billion by 2023.
\item In 2020, Google and Facebook accounted for 60\% of the global digital advertising market.
\item The data brokerage industry, which includes companies that collect and sell personal data, is estimated to be worth \$200 billion.
\item In 2020, Google and Facebook were reported to have data on over 4 billion active users.
\item As of 2021, the number of data breaches reported worldwide has grown from 4.1 billion in 2018 to 4.9 billion in 2020.
\item In 2013, it was revealed that the US National Security Agency (NSA) had been collecting the phone records of millions of Americans under its PRISM program.
\item In 2013, Edward Snowden leaked classified documents that revealed the scale of the NSA's surveillance programs.
\item In the US, the Foreign Intelligence Surveillance Act (FISA) allows the government to conduct surveillance on non-US citizens outside the US without a warrant.
\item The UK's Investigatory Powers Act 2016, also known as the "snooper's charter," gives government agencies wide-ranging powers to collect and analyze personal data.
\item In 2021, it was reported that the Chinese government has been collecting and analyzing the data of its citizens through a system of "social credit" scores, which are used to monitor and control individuals' behaviour.
\item Surveillance capitalism refers to the business model of collecting and analyzing personal data for the purpose of targeted advertising and other forms of monetization.
\item A recent study by the Center for Digital Democracy found that the top 100 global digital media companies are projected to generate over \$1 trillion in revenue by 2020, much of which is derived from surveillance-based advertising.
\item The number of surveillance cameras in use worldwide is estimated to be over 1 billion, with the majority located in China.
\item A 2018 study by Comparitech found that the average person in the UK is captured on CCTV cameras over 300 times per day.
\item According to a report by the American Civil Liberties Union (ACLU), the FBI has access to over 640 million photographs for facial recognition searches, including driver's license and passport photos.
\item The U.S. government's use of surveillance technologies, such as drones and mass data collection, has been a subject of ongoing controversy and debate.
\item Some experts warn that the increasing use of surveillance technologies by governments and private companies could lead to the erosion of privacy rights and the creation of a "surveillance state."
\item In the USA senate hearing following the collapse of FTX Rep. Jesus Garcia described bitcoin and crypto as an industry that operates outside of the law and relies on hype, implying that the communities that have adopted bitcoin are ill-informed and vulnerable.
\item Bitcoin has been adopted by a variety of communities worldwide, particularly in countries such as Vietnam, the Philippines, Ukraine, India, Pakistan, Brazil, Thailand, Russia, and China.
\item There is an outsized level of adoption among Black Americans in the United States. This trend is not a result of targeted advertising by companies such as FTX, but rather a response to a legacy financial system that has limited individuals' potential.
\item Marginalized early adopters of bitcoin still constitute a minority in their communities, but the worldwide adoption trend among these groups is on the rise.
\item The solutions that outsiders build in bitcoin will ultimately be the source of the technology's promised revolution. Adoption in Africa and possibly India seems likely to be capable of driving this.
\item The paradigm shift will come from those who bring local, real-world focused use cases to their communities, separating bitcoin from the empty hype of speculation.
\item Marginalized communities will lead the industry's recovery and redefine the purpose of bitcoin in the future.
\end{itemize} 

Much of the following text is paraphrased from the work of Guy Turner of `The Coin Bureau', and Lawyer and academic Eden Moglen, and needs more work because of it's critical importance to the book.\par 
The adoption of printing by Europeans in the 15th century led to concerns around access to printed material. The right to read and the right to publish were central subjects in the struggle for freedom of thought for most of the last half millennium. The basic concern was for the right to read in private and to think, speak, and act based on a free and uncensored will. The primary antagonist for freedom of thought at the beginning of this struggle was the universal Catholic Church, an institution aimed at controlling thought in the European world through weekly surveillance of individuals, censorship of all reading material, and the ability to predict and punish unorthodox thought. In early modern Europe, the tools available for thought control were limited, but they were effective. For hundreds of years, the struggle centered around the book as a mass-manufactured article in Western culture, and whether individuals could print, possess, traffic, read, or teach from books without the permission or control of an entity empowered to punish thought. By the end of the 17th century, censorship of written material in Europe began to break down in waves throughout the European world, and the book became an article of subversive commerce, undermining the control of thought.\par
Currently, a new phase in human history is beginning as we are building a single extraneous digital nervous system, that will connect every human mind. Within two generations, every single human being will be connected to this network, in which all thoughts, plans, dreams, and actions will flow as nervous impulses. The fate of freedom of thought and human freedom as a whole will depend upon the organization of this network. Our current generation is the last in which human brains will be formed without contact with this network, and from now on, every human brain will be formed from early life in direct connection to the network, with input from generative AI/ML systems. This possibly results in humanity becoming a super organism of a sort, where each of us is but a neuron in the brain. Unfortunately, this generation has been raised to be consumers of media, which is now consuming us.\par Anonymous reading is being determined against. Efforts discussed throughout the book to ensure privacy, from Zimmerman and the cypherpunks onward, have been met with resistance from government efforts to monitor and control information flow. The outcome of the organization of this network, and the freedom it allows, is currently being decided by this generation.\par
It is not solely the ease of surveillance, nor solely the permanence of data, that is concerning, it is the relentless nature of living after the ``end of forgetting''. Today's encrypted traffic, which is used with relative security, will eventually be decrypted as more data becomes available for crypto analysis. This means that security protocols will need to be constantly updated and redone. Furthermore, no information is ever truly lost, and every piece of information can be retained and eventually linked to other information. This is the rationale behind government officials who argue that a robust social graph of the United States is needed. The primary form of data collection that should be of most concern is media that is used to spy on us, such as books that watch us read them and search boxes that report our searches to unknown parties. There is a lot of discussion about data coming out of Meta/Facebook, but the true threat is code going in. For the past 15 years, enterprise computing has been adding a layer of analytics on top of data warehouses, which is known as business intelligence. This allows for the vast amount of data in a company's possession to be analyzed and used to answer questions the company did not know it had. The real threat of Facebook is the business intelligence layer on top of the Facebook data warehouse, which contains the behaviour of nearly a billion people. Intelligence agencies from around the world want to access this layer in order to find specific classes of people, such as potential agents, sources, and individuals that can be influenced or tortured. The goal is to run code within Facebook to extract this information, instead of obtaining data from Facebook, which would be dead data once extracted. Facebook wants to be a media company and control the web, but the reality is the true value of Facebook is the information and behavior of it's users, and the ability to mine that data.
Distributed internet protocols are important in the context of government overreach into digital society and people's private lives because they provide a level of decentralization and resilience that can help protect against censorship and surveillance.\par
For example, if a government were to attempt to censor or block access to a centralized internet service, it could potentially do so with relative ease. However, if that same service were distributed across a network of nodes, it would be much more difficult for the government to effectively censor or block access to it.\par
Another advantage of distributed protocols is that they are typically more resilient to attacks or failures. If one node in the network goes offline or is compromised, the others can continue to operate, ensuring that the service remains available. This can be especially important in situations where the internet is being used for critical communication, such as during a natural disaster or political crisis.\par
In addition to their benefits for censorship resistance and resilience, distributed protocols can also help protect people's privacy. Because they do not rely on centralized servers or infrastructure, they can be more difficult for governments or other entities to monitor or track. This can be especially important in countries where government surveillance is prevalent or where individuals may be at risk of persecution for their online activities.\par 
There are a number of distributed protocols that have been developed specifically to address issues of censorship and privacy, and these will be covered in more detail later.\par
It is important to note that distributed protocols are not a silver bullet for censorship or privacy concerns. They can be vulnerable to certain types of attacks, such as those that target the nodes of the network, and they may not always be practical for certain types of applications. However, they do provide an important tool for those seeking to protect their freedom of expression and privacy online. They offer a valuable tool for those seeking to protect their freedom of expression and privacy online, and they will likely continue to play a critical role in the future of the internet.\par
In recent years, several countries have proposed or passed bills that would result in unprecedented levels of online censorship. One such example is Canada's Bill C-11, also known as the Online Streaming Act. This bill was first proposed in November 2020 as Bill C-10, but failed to pass due to its controversial provisions. It was reintroduced in February 2021 as Bill C-11 and was approved by the Canadian House of Commons, the first step in the process of becoming law. If passed, the bill would give the Canadian Radio, Television and Telecommunications Commission (CRTC) the power to decide what content Canadians can view on YouTube and other social media platforms. The CRTC would also have the power to dictate what content creators can produce, with a focus on promoting "Canadian content." Additionally, the bill would require certain broadcasters to contribute to the Canada Media Fund, which is used to fund mainstream media in Canada. The bill is currently being considered by the Canadian Senate, which will vote on it in February. If passed, it will then be debated by the Canadian Parliament. Tech companies such as YouTube have reportedly failed to convince the Senate to exclude user-generated content from the bill, indicating a high likelihood of it becoming law. The potential impact on the internet and free expression in Canada is significant, as the bill would give the government significant control over online content and restrict the ability of individuals to share their views and perspectives.\par
The European Union (EU) has separated its online censorship efforts into two separate bills: the Digital Markets Act and the Digital Services Act. These bills were introduced in December 2020 and are part of the EU's Digital Services package, which aims to be completed by 2030. The Digital Services package is the second phase of the EU's digital agenda, which is being enforced through regulation in the public sector and through ESG investing in the private sector. Both the Digital Markets Act and the Digital Services Act were passed in spring 2022 and went into force in autumn 2022, but will not be enforced until later this year and early next year, depending on the size of the relevant entity. The Digital Markets Act aims to increase the EU's competitiveness in the tech space by imposing massive fines on "gatekeepers," or companies that maintain monopolies by giving preference to their own products and services. This could open the door to innovation in cryptocurrency in the EU, but also requires gatekeepers to provide detailed data about the individuals and institutions using their products and services to the EU. The Digital Services Act, on the other hand, aims to regulate the content that is available online, including user-generated content. It does this by requiring companies to remove illegal content within one hour of it being reported and by imposing fines for non-compliance. The act also requires companies to implement measures to protect users from illegal content and from "other forms of harm," which is defined broadly and could include a wide range of content. The EU is also in the process of passing the Artificial Intelligence Regulation Act, which will be discussed later this year and is reportedly the first of its kind. All five bills in the EU's Digital Services package are regulations, meaning they will override the national laws of EU countries. The potential impact on the internet and free expression in the EU is significant, as the Digital Services Act would give the government significant control over online content and restrict the ability of individuals to share their views and perspectives.\par
In the United States, two significant documents related to online censorship are the Kids Online Safety Act and the Supreme Court case Gonzalez v. Google. The Kids Online Safety Act was introduced in February 2021 and is expected to pass later this year due to bipartisan support. The act requires online services to collect Know Your Customer (KYC) information to ensure that they are not showing harmful content to minors. It also gives the Federal Trade Commission (FTC) the power to decide when children have been made unsafe online and allows parents to sue tech companies if their children have been harmed online. The act has received criticism from both sides of the political spectrum and entities outside of Congress, as it is seen as giving too much power to the government to regulate online content and could lead to increased censorship by tech companies.\par
The Supreme Court case Gonzalez v. Google involves the question of whether Google's algorithmic recommendations supported terrorism and contributed to the 2015 terrorist attacks in Paris. The case has been picked up by the Supreme Court after being passed up by various courts of appeal. It is being heard alongside another case, Twitter v. Tumne, involving the role of Twitter's algorithms in a terrorist attack in Istanbul. There are two potential outcomes for the case. If the Supreme Court sides with Gonzalez, it could increase the liability of social media companies under Section 230 of the Communications Decency Act, which allows them to moderate content to a limited extent without violating the First Amendment. Alternatively, the Supreme Court could declare Section 230 unconstitutional, which would make online censorship illegal but also hinder the use of algorithms on the internet. The ideal outcome, in theory, would be for the Supreme Court to side with Google and for Congress to change Section 230. However, giving Congress the power to change the law could lead to increased censorship and the potential for abuse of power.\par
In the UK forthcoming legislation will see tech company leaders liable for \href{https://www.independent.co.uk/news/uk/politics/bill-mps-iain-duncan-smith-molly-russell-rishi-sunak-b2263353.html}{prison sentences} if they fail in their duty to protect minors. This will doubtless lead to both stringent universal requirements for identity proof (KYC), and significantly muted and controlled content on the platforms.\par
Our research focuses on business to business use cases for distributed technologies, and will provide mechanisms for verifying who is communicating with whom, to avoid falling foul of these swinging global infringements on privacy.\par
It is the opinion of this book that information should be free \cite{swartz2008guerilla}
\section{Opportunities in Africa, and Gridless}
In the course of researching this book we see most opportunity for change in Africa. As an example the company `Gridless' began by examining different energy sources in Africa and exploring opportunities for larger energy generation and grid-connected energy. However, they found that the real benefit of gridless energy was in providing energy to places that were not well connected and did not have a good grid. They contacted mini-grid providers all over East and Southern Africa to learn about their problems. A mini-grid is defined as a project that generates energy under 2 megawatts, often under 1 megawatt. They discovered that these providers had to overbuild for the community, resulting in stranded energy. The company found a way to utilize this stranded energy by placing Bitcoin miners on it and paying the mini-grid providers for it. They tested this method and found it to be successful. Additionally, they implemented a system to automate and remotely turn off the power during periods of high usage to make the grid more efficient and sustainable. This solution provided a win-win-win situation for the company, the mini-grid providers, and the communities they served.\par
The company utilizes Bitcoin miners to create space for other activities and to increase access to affordable energy for communities and small businesses. As energy usage increases in the community, the company decreases their usage of miners and moves them to other locations. This is outlined in their contracts with partners. The company is currently testing this method and has encountered some challenges, such as losing internet connection at one of their sites and poor rainfall affecting the amount of water flowing into turbines. They have found that building a lean operation with flexible and adaptable staff is crucial, as well as creating processes and systems to manage variables. The company also faces unique environmental factors such as lightning strikes, which require them to turn off their operations temporarily.\par
Gridless suggest that those who are critical of opportunities like this often come from a place of privilege and do not understand the consequences of their actions in places like Africa where access to electricity and other resources is limited. They argue that these critics, who are often from the West, have blinders on and cannot see the impact of their actions on a global scale. They suggest that more people need to travel and have diverse experiences in order to change their perspective on Bitcoin and its potential to support human flourishing in underprivileged areas. They also mention that gridless plans may become a case study for the positive impact of Bitcoin mining on economic opportunities, particularly in rural Africa.